---
title: "C+T_1009"
author: "Chengyan Ji"
date: "2024-10-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**10/09: This is C+T for fastGWA and GWASPlink2.0 with only sex as covariate, phenotype: trans_harm2, QCed data**
**10/09: This task uses the new directory system**
**10/09: Add readme and SNPcounts**
**10/09: Structure: bfile_by_chr --> Thresholding(pvalthr) --> save results(pvalthr) --> clumping(pvalthr)**
**10/09: Will introduce duplicates if all content not removed before running**
**10/09: Current readme in C+Ted folder will only show ROIs with no significant SNPs after C+T, but not show which ROI has no GWAS results, please original GWAS folder readme**
**02/06: yao想要另一个threshold的C+T: 0.6+1.31926e-10**

```{r}
library(optparse)
library(parallel)
library(readr)
library(bigreadr)
library(bigsnpr)
library(data.table)
library(dplyr)
library(metafor)

### Define directories==========================================================
in_dir <- "/Users/kurt/Documents/Data_Science_Project/1008_GWAS/"
directory <- "/Users/kurt/Documents/Data_Science_Project/1009_MR/"
plink_path <- paste0("/Users/kurt/Documents/Data_Science_Project/Tools/", "plink")
bfile_path <- paste0("/Users/kurt/Documents/Data_Science_Project/ABCD_data/", "ABCD_bfile/bfile_for_gwas_comparison/")

### Set Parameters==============================================================
# Input:
NCORES = 1 # Number of cores used for training lassosum2 models under different tuning parameter settings.
# Parameters for the Clumping step
kb = 500 # SNPs within 500kb of the index SNP are considered for clumping
p.ldclump = 0.6 #0.5 # LD p-value threshold for a SNP to be included as an index SNP # 0206: Yao要一个版本的
pvalthrs = c(1.31926e-10) #c(5e-08) #c(5e-06, 5e-07, 5e-08) # p-value threshold for thresholding
r2 = 0.001 # SNPs having r2 higher than 0.1 with the index SNPs will be removed # optional: c(0.1,0.2,0.4,0.6,0.8)

trait_name <- "adhd" ## This is not used
method <- 'method_0206new' ## I AM NOT SURE WHAT THIS IS ## there was a variable called "method" but never used in the original code
ite <- 1 ## I AM NOT SURE WHAT THIS IS

#========================================================================================================================  
#========================================================================================================================  

QCs <- c("_qc") # qc and no qc: "_noqc"
unrels <- c("_unrelated") #c("_unrelated") # all obs and unrelated obs
harms <- c("_sd_harm2") # harm2 and fisher+harm2
methods <- c("gwasplink20_covsex_yao") # c("fastGWA_covsex", "")
rois <- (1:379)

################################################### For Loop 1 Begins ###################################################
for (qc in QCs) {
  for (unrel in unrels) {
    #-----------get bfile---------------------------------------------------------
    bfile <- paste0(bfile_path, "scfc_all", qc, unrel)
    for (harm in harms) {
      for (method in methods) {
        #------------------Get directory for storing GWAS results---------------
        gwas_dir <- paste0(in_dir, method, qc, unrel, harm, "/gwas_results_csv/")
        #------------------Set up directory to save MR results------------------
        work_dir <- paste0(directory, method, qc, unrel, harm, "_MR/")
        if (!dir.exists(work_dir)) { dir.create(work_dir, recursive = F) }
        #=============Create directories for C+T========================================
        #-------------1st level directories---------------------------------------------
        # 1.1: for storing bfile by chr, same for all pvalthr
        if (!dir.exists(paste0(work_dir, "bfile_by_chr/"))) { dir.create(paste0(work_dir, "bfile_by_chr/"), recursive = F) }
        # 1.2: for storing C+T results (contain parallel Thresholding, Clumping and C+T directories)
        ct_results_path <- paste0(work_dir, "C+T/") 
        if (!dir.exists(ct_results_path)) { dir.create(ct_results_path, recursive = F) }
        # 1.3: beneath C+T/: Thresholding, Clumping and C+T
        thresh_path <- paste0(work_dir, "C+T/Thresholding/") # 1.3.1: Thresholding results
        if (!dir.exists(thresh_path)) { dir.create(thresh_path, recursive = F) }
        clumping_path <- paste0(work_dir, "C+T/Clumping/")   # 1.3.2: Clumping results
        if (!dir.exists(clumping_path)) { dir.create(clumping_path, recursive = F) }
        ct_path <- paste0(work_dir, "C+T/C+Ted_", method, qc, unrel, harm, "/")            # 1.3.3: Processed C+T results containing SNP and test results
        if (!dir.exists(ct_path)) { dir.create(ct_path, recursive = F) }
        
        ## I. Break geno files by CHRs (ABCD actually comes separated but QC combined them) and store to "bfile_by_chr/"
        for (chr in 1:22) {
          output_path <- paste0('"', work_dir, "bfile_by_chr/scfc_all", qc, unrel, "_chr", chr, '"')
          command <- paste(plink_path, "--bfile", bfile, "--chr", chr, "--make-bed --out", output_path)
          system(command, intern=TRUE)
        }

        for (roi in rois) {
          #==============================read GWAS results==============================
          # Either a fastGWA file, a PLINK2.0, or a PLINK1.9 file
          gwas_path <- paste0(gwas_dir, method, qc, unrel, "_scfc", harm, "_fam_roi", roi, ".csv")
          if (!file.exists(gwas_path)) {
            cat("No GWAS results available for roi:", roi, "skipping current roi...")
            next
          }
          # # alternative way might be useful in the future: not read csv, just read original gwas output
          # fastGWA_path <- paste0(gwas_dir, "fastGWA_roi", roi, ".fastGWA")
          # gwas20_path <- paste0(gwas_dir, "gwas_scfc_unrelated_sd_harm2_family_roi", roi, ".PHENO1.glm.linear")
          # gwas19_path <- paste0(gwas_dir, "gwasplink19_roi", roi, ".qassoc")
          #-----------------------------------------------------------------------------
          if (startsWith(method, "fastGWA")) {
            cat("\n\nroi",roi,":fastGWA")
            gwas_roi <- read.csv(gwas_path, header = TRUE) %>%
              rename(A1_fastgwa = A1, A2_fastgwa = A2, AF1_fastgwa = AF1) %>%
              mutate(REF_plink = NA, ALT_plink = NA, PROVISIONAL_REF_plink = NA, A1_plink = NA, OMITTED_plink = NA, AF1_plink = NA) %>% # Add empty columns for PLINK-specific fields
              select(CHR, SNP, POS, REF_plink, ALT_plink, PROVISIONAL_REF_plink, A1_plink, OMITTED_plink, AF1_plink, A1_fastgwa, A2_fastgwa, AF1_fastgwa, N, BETA, SE, P) # only keep necessary columns (both plink and fastgwa columns are kept)
            
          } else if (startsWith(method, "gwasplink20")) {
            cat("\n\nroi",roi,":GWAS plink2.0")
            gwas_roi <- read.csv(gwas_path, header = TRUE) %>% # The chrome column name keeps changing names i don't know why
              rename(CHR = `X.CHROM`, REF_plink = REF, ALT_plink = ALT, PROVISIONAL_REF_plink = `PROVISIONAL_REF.`, A1_plink = A1, OMITTED_plink = OMITTED, AF1_plink = A1_FREQ, N = OBS_CT) %>%
              mutate(A1_fastgwa = NA, A2_fastgwa = NA, AF1_fastgwa = NA) %>% # Add empty columns for FastGWA-specific fields
              select(CHR, SNP, POS, REF_plink, ALT_plink, PROVISIONAL_REF_plink, A1_plink, OMITTED_plink, AF1_plink, A1_fastgwa, A2_fastgwa, AF1_fastgwa, N, BETA, SE, P) # only keep necessary columns (both plink and fastgwa columns are kept)
            
          } else if (startsWith(method, "gwasplink19")) {
            cat("\n\nroi",roi,":GWAS plink1.9")
            gwas_roi <- read.csv(gwas_path, header = TRUE) %>%
              rename(POS = BP, N = NMISS) %>%
              select(CHR, SNP, POS, N, BETA, SE, P)
            
          } else {
            cat("\nDid you type in the wrong method name? Current GWAS method does not have result files available for ROI", roi, "\n")
            next  # Skip to the next iteration if no files are found
          }
          #-----------------------------------------------------------------------------
          #### IV Selection (using exposure: scfc)######################################
          ### Run T+C (Thresholding first and Clumping next)============================
          for (pvalthr in pvalthrs) {
            # -----for inspection purpose, output thresholding results to local---------
            gwas_roi.thresh <- gwas_roi[gwas_roi$P <= pvalthr,]
            thresh_count_path <- paste0(thresh_path, "threshold_count/", method, qc, unrel, "_", pvalthr, "/")
            if (!dir.exists(thresh_count_path)) { dir.create(thresh_count_path, recursive = TRUE) }
            write.table(gwas_roi.thresh, paste0(thresh_count_path, "gwas_thresh_roi",roi,".txt"), row.names = F, col.names = T, quote = F)
            readme_path <- paste0(thresh_count_path, "readme.txt")
            readme_conn <- file(readme_path, "a")
            writeLines(paste0("roi", roi, " after thresholding: ", nrow(gwas_roi.thresh)), readme_conn)
            close(readme_conn)
            
            ## ---------------------2nd level Directories-------------------------------
            ## 2.1 Thresholding
            thresh_idlist_path <- paste0(thresh_path, "thr_idlists/")                   # 2.1.1 for storing SNP id lists for plink to subset bfiles
            if (!dir.exists(thresh_idlist_path)) { dir.create(thresh_idlist_path, recursive = F) }
            thresh_bfile_by_chr_path <- paste0(thresh_path, "thr_bfile_by_chr/")        # 2.1.2 for storing bfile by chr AFTER thresholding (for clumping)
            if (!dir.exists(thresh_bfile_by_chr_path)) { dir.create(thresh_bfile_by_chr_path, recursive = F) }
            thresh_gwas_path <- paste0(thresh_path, "thr_gwas/")                           # 2.1.3 for storing GWAS results filtered AFTER thresholding (for clumping) 
            if (!dir.exists(thresh_gwas_path)) { dir.create(thresh_gwas_path, recursive = F) }
            
            ## 2.2 Clumping
            clump_clumped_path <- paste0(clumping_path, "clumped/")                     # 2.2.1 for storing raw clumped results, by chr
            if (!dir.exists(clump_clumped_path)) { dir.create(clump_clumped_path, recursive = F) }
            
            ## 2.3 C+T does not need additional sub-directories
            
            ## --------------------3rd level Directories (pvalthr)----------------------
            # create directories for thresholding p-values (pvalthr)
            # 2.1.1 thresholding directories
            thresh_idlist_pvalthr_path <- paste0(thresh_idlist_path, "idlist_p=", pvalthr, "/")                    # 2.1.1.1 for storing SNP id lists for current pvalthr
            if (!dir.exists(thresh_idlist_pvalthr_path)) { dir.create(thresh_idlist_pvalthr_path, recursive = F) }
            thresh_bfile_by_chr_pvalthr_path <- paste0(thresh_bfile_by_chr_path, "bfile_by_chr_p=", pvalthr, "/")  # 2.1.2.1 for storing bfiles for current pvalthr
            if (!dir.exists(thresh_bfile_by_chr_pvalthr_path)) { dir.create(thresh_bfile_by_chr_pvalthr_path, recursive = F) }
            thresh_gwas_pvalthr_path <- paste0(thresh_gwas_path, "gwas_p=", pvalthr, "/")                          # 2.1.3.1 for storing GWAS results for current pvalthr
            if (!dir.exists(thresh_gwas_pvalthr_path)) { dir.create(thresh_gwas_pvalthr_path, recursive = F) }
            
            # 2.2.1 clumping directories
            clump_clumped_pvalthr_path <- paste0(clump_clumped_path, "clumped_p=", pvalthr, "/")                 # 2.2.1.1 for storing raw clumped results for current pvalthr
            if (!dir.exists(clump_clumped_pvalthr_path)) { dir.create(clump_clumped_pvalthr_path, recursive = F) }
            
            # 2.3.1 C+T directories
            ct_pvalthr_path <- paste0(ct_path, "p=", pvalthr, "/")                                                 # 2.3.1.1 for storing C+T results for current pvalthr 
            if (!dir.exists(ct_pvalthr_path)) { dir.create(ct_pvalthr_path, recursive = F) }
            ct_final_path <- paste0(ct_pvalthr_path, 'roi', roi, '.', "_p=", pvalthr, "_r2=", r2, ".txt")          # 2.3.1.2 txt file for storing final C+T SNPs, used if clumping is successful
        
            #---------------------------------------------------------------------------
            for (chr in 1:22){
        
              sum.chrspecific = gwas_roi[gwas_roi$CHR == chr,]
              # --------------------- Step 2.2: Run C+T --------------------------------
              set.seed(2023)
              
              ## --------------------- Thresholding (T) --------------------------------
              # filter SNPs by p-value
              sum.data <- sum.chrspecific
              sum.data <- sum.data[sum.data$P <= pvalthr,]
              # writes list of filtered SNP id
              snp_id_list <- paste0(thresh_idlist_pvalthr_path, "idlist_roi",roi,'_chr',chr,'_pvalthr',pvalthr,".txt") #这个filtered指的是thresholding
              write.table(sum.data[,'SNP'], snp_id_list, quote = F, col.names = F, row.names = F)
              
              # write filtered SNPs bfile back to SNP list using PLINK1.9
              system(paste0(plink_path, " --bfile ", work_dir, "bfile_by_chr/scfc_all", qc, unrel, "_chr", chr,
                            " --extract ", snp_id_list,
                            " --make-bed --out ", thresh_bfile_by_chr_pvalthr_path, "scfc_all", qc, unrel, "_thr","_roi",roi,'_chr',chr,'_pvalthr',pvalthr), # filtered snps by chr
                     intern = T)
              
              # write the threshold GWAS summary with SNP and P-value to local (to be used by clumping)
              sumstats_input <- sum.data[,c('SNP','P')]
              fwrite(sumstats_input, file=paste0(thresh_gwas_pvalthr_path,'gwas_roi',roi,'_chr',chr,'_pvalthr',pvalthr,'.txt'),row.names = F, quote = F, sep=' ')
              
              cat('\nTHRESHOLDING FINISHED roi:',roi,' chr:',chr," pvalthr:",pvalthr)
              
              ## --------------------- LD Clumping (C) ---------------------
              # outputfilename
              clumpedfilename <- paste0("roi",roi,'_chr',chr,"_clumped") # C+T files naming: removed "adhd" in the name, removed "ite", put "roi" before "chr"
              # run clumping on plink
              ldclumpcode <- paste0(plink_path, 
                                    ' --bfile ',thresh_bfile_by_chr_pvalthr_path,"scfc_all",qc,unrel,"_thr","_roi",roi,'_chr',chr,'_pvalthr',pvalthr,
                                    ' --clump ',thresh_gwas_pvalthr_path,'gwas_roi',roi,'_chr',chr,'_pvalthr',pvalthr,'.txt',
                                    ' --clump-p1 ',p.ldclump,
                                    ' --clump-r2 ',r2,
                                    ' --clump-kb ',kb,
                                    ' --threads 1',
                                    # ' --silent',
                                    ' --out ',clump_clumped_pvalthr_path,clumpedfilename)
              system(ldclumpcode, intern = T)
              cat('\nCLUMPING FINISHED roi:',roi,' chr:',chr," pvalthr:",pvalthr)
              
              ##===================== read clumped files================================
              # First confirm that there is valid clumped results
              if (!file.exists(paste0(clump_clumped_pvalthr_path,clumpedfilename,'.clumped'))) {
                cat('\nNO CLUMPING RESULTS AVAILABLE for roi:',roi,' chr:',chr," pvalthr:",pvalthr)
                next
              }
              LD <- bigreadr::fread2(paste0(clump_clumped_pvalthr_path,clumpedfilename,'.clumped'))
              clump.snp <- LD[,3,drop=F]
              prs.all <- left_join(clump.snp,sum.data,by="SNP")
              
              prs.file = prs.all[prs.all$P <= pvalthr,] # USELESS?
              # -------------------------- Append the SNPs by chr ----------------------
              if (file.exists(ct_final_path)) {
                write.table(prs.file, file = ct_final_path, append = TRUE, col.names = FALSE, row.names = F, quote = F)
              } else {
                write.table(prs.file, file = ct_final_path, append = FALSE, col.names = TRUE, row.names = F, quote = F)
              }
              cat('\nC+T DONE for roi:',roi,' chr:',chr," pvalthr:", pvalthr)
            }
            # ------for inspection purpose, output C+T counts results to local----------
            readme_path <- paste0(ct_pvalthr_path, "readme.txt")
            readme_conn <- file(readme_path, "a")
            if (file.exists(ct_final_path)) {
              ct.count <- read.table(ct_final_path, header = T)
              writeLines(paste0("roi", roi, " after C+T: ", nrow(ct.count)), readme_conn)
            } else {
              writeLines(paste0("roi", roi, " after C+T: ", "No SNPs pass C+T"), readme_conn)
            }
            close(readme_conn)
          }
        ####
        }
      }
    }
  }
}
```
