---
title: "ivreg_1102"
author: "Chengyan Ji"
date: "2025-01-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**10/05: IV Regression using GWAS plink1.9 results (with fisher transform). This is a redo for previous MR analysis**
**10/05: 3 thresholding level results used**
**10/05: Uses new directory system (first time using the "Phenotype" directory for MR analysis)**
**11/02: Runnign IVReg with Binary ADHD diagnosis with PLINK1.9 GWAS results for SCFC**
**11/03: Need to change IVReg**
**11/04：Now use 2SRI**
**01/06: Redo using GWAS plink2.0 results sex unrelated.**
**01/06: For original plink19 run, C+T was redone, but here C+T results come directly from 1009_MR results**
**02/24: Redo by including t statistics**

```{r}
# # Define the directory containing the files
# base_dir <- "/Users/grc8mu/Desktop/DS/1102_MR/gwasplink19_qc_sd_harm2/gwas_results_csv"  # Replace with your actual path
# 
# # Loop through each file from 1 to 379 and rename
# for (k in 1:379) {
#   old_filename <- paste0("gwasplink19_roi", k, ".csv")
#   new_filename <- paste0("gwasplink19_qc_scfc_sd_harm2_fam_roi", k, ".csv")
#   
#   # Define the full paths for renaming
#   old_path <- file.path(base_dir, old_filename)
#   new_path <- file.path(base_dir, new_filename)
#   
#   # Check if the old file exists, then rename
#   if (file.exists(old_path)) {
#     file.rename(old_path, new_path)
#     cat("Renamed", old_filename, "to", new_filename, "\n")
#   } else {
#     cat(old_filename, "does not exist.\n")
#   }
# }

```

## 
```{r}
library(snpStats)
library(tibble)
library(dplyr)
library(AER)
library(readxl)

trait_name <- 'ADHD'                    # trait name
pvalthrs <- c(5e-08)      # thresholds                 
qc <- "_qc"                             # whether bfile used is QCed
gwas <- "gwasplink20sexunrel"                   # corresponds to 1008 GWAS using PLINK2.0 with fisher transformed SCFC and with sex and unrelated samples
r2 <-0.001

### Load Utilities, data, tool and define directory
utilities_path <- "/Users/grc8mu/Desktop/DS/ABCD_data/ABCD_SCFC_utilities/"
bfile_path <- "/Users/grc8mu/Desktop/DS/ABCD_data/ABCD_bfile/bfile_for_gwas_comparison/"
cov_path <- "/Users/grc8mu/Desktop/DS/ABCD_data/Covariates/"
harm_path <- "/Users/grc8mu/Desktop/DS/ABCD_data/Harmonized_scfc/"
pheno_path <- "/Users/grc8mu/Desktop/DS/ABCD_data/Phenotype/"
tool_path <- "/Users/grc8mu/Desktop/DS/Tools/"

if (qc == "_qc") { bfile_path <- paste0(bfile_path,"scfc_all_qc_unrelated") # read bfile
} else { bfile_path <- paste0(bfile_path,"scfc_all_noqc_unrelated") }

directory <- "/Users/grc8mu/Desktop/DS/20250106_MR_Diag_Redo/gwasplink20_covsex_qc_unrelated_sd_harm2_MR/"                    # directory for task
ct_path <- paste0(directory, "C+T/C+Ted/")                                                                         # directory for C+T results
mr_dir <- paste0("/Users/grc8mu/Desktop/DS/20250106_MR_Diag_Redo/mr_one_sample_", trait_name, "/") # directory for storing mr results
work_dir <- paste0(mr_dir, "ivreg_gwasplink20sexunrel/")                                                                   # directory for storing current mr task results
if (!dir.exists(mr_dir)) { dir.create(mr_dir, recursive = F) }
if (!dir.exists(work_dir)) { dir.create(work_dir, recursive = F) }

load(paste0(utilities_path, "coupling_cbcl.RData"))
load(paste0(utilities_path, "scfc_coupling_matched.RData"))

## This step is not entirely necessary, only aiming to proof read the id correspondence
#-------------------------------------------------------------------------------
new_fam <- read.table(paste0(utilities_path, "acspsw03.txt"), header=T) %>%       # get new fam id; this step is not necessary as the .fam files already uses new fam ids, just verifying
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(rel_family_id, subjectkey) %>%
  rename(fid = rel_family_id, iid = subjectkey) %>%
  mutate(fid = as.integer(fid))
cbcl_fam <- read.csv(paste0(utilities_path, "demo_cbcl_baseline_n11876.csv")) %>% # get cbcl iid;
  select(subjectkey) %>%
  rename(iid = subjectkey)
old_bfile_fam <- read.table(paste0(substring(bfile_path, 1, (nchar(bfile_path) - 21)), "ABCD_all_old.fam")) %>%           # get old bfile fam id
  select(V1, V2) %>%
  rename(fid_old = V1, iid = V2)
scfc_fam <- demo_cbcl_base_scfc %>%                                               # get scfc id
  select(subjectkey) %>%  
  mutate(subjectkey = sub("^(.{4})", "\\1_", subjectkey)) %>%
  rename(iid = subjectkey)
bfile_fam <- read.table(paste0(bfile_path, ".fam")) %>%                           # get current bfile fam id
  select(V1, V2) %>%
  rename(fid = V1, iid = V2)

# get id correspondence
id_list <- new_fam %>%
  inner_join(cbcl_fam, by = "iid") %>%
  inner_join(old_bfile_fam, by = "iid") %>%
  inner_join(scfc_fam, by = "iid") %>%
  inner_join(bfile_fam, by = c("iid", "fid"))
#-------------------------------------------------------------------------------

## ------------------------read outcome and covariates--------------------------
# Load the diagnosis dataset
dsm5_diag <- read_excel(paste0(utilities_path, "abcd_diagnosis_sum_baseline_n11976.xlsx"))
dsm5_diag <- dsm5_diag %>%
  select(subjectkey, ADHD, Dep, Bip, DMDD, Schi, Anx, OCD, Eat, ODD, Cond, PTSD) %>%
  rename(iid = subjectkey) %>%
  inner_join((id_list %>% select(fid, iid)), by = "iid") %>%
  select(fid, iid, ADHD, Dep, Bip, DMDD, Schi, Anx, OCD, Eat, ODD, Cond, PTSD)

df_outcome <- dsm5_diag %>% # Read outcome
  #select(subjectkey, cbcl_scr_dsm5_depress_t, cbcl_scr_dsm5_anxdisord_t, cbcl_scr_dsm5_somaticpr_t, cbcl_scr_dsm5_adhd_t, cbcl_scr_dsm5_opposit_t, cbcl_scr_dsm5_conduct_t) %>%
  rename(outcome = paste0("",trait_name,"")) %>%
  #mutate(iid = sub("^(.{4})", "\\1_", iid)) %>%
  #inner_join(id_list, by = c("iid")) %>%
  select(fid, iid, outcome)

CFDRs <- demo_cbcl_base_scfc %>% # get covariates
  select(subjectkey, site_id_l, interview_age, sex, race, ethn) %>%
  mutate(
    iid = sub("^(.{4})", "\\1_", subjectkey)  # Add '_' after the 4th character
    #ethn = as.factor(ethn),  # Convert ethnicity factor if needed
    #race = as.factor(race)   # Convert race factor if needed
  ) %>%
  inner_join(id_list, by = c("iid")) %>%
  select(fid, iid, site_id_l, interview_age, sex, race, ethn) %>%
  mutate(  # deal with spaces in variables
    race = gsub(" ", "_", race),                      # Replace spaces in 'race'
    ethn = gsub(" ", "_", ethn)                       # Replace spaces in 'ethnicity'
  )
# Fill NAs in race and ethnicity with mode
calculate_mode <- function(x) {
  ux <- unique(na.omit(x))  # Remove NA values before finding the mode
  ux[which.max(tabulate(match(x, ux)))]
}
CFDRs$race <- ifelse(is.na(CFDRs$race), calculate_mode(CFDRs$race), CFDRs$race)
CFDRs$ethn <- ifelse(is.na(CFDRs$ethn), calculate_mode(CFDRs$ethn), CFDRs$ethn)

df_out_cov <- left_join(df_outcome, CFDRs, by = c("fid", "iid")) # Merge with covariates
#-------------------------------------------------------------------------------
```

## Remove NAs in df
```{r}
# Filter out rows where 'outcome' is not 0 or 1
df_out_cov <- df_out_cov %>%
  filter(outcome %in% c(0, 1))
```

```{r}
# A small sample
# Load necessary libraries
library(dplyr)
library(tibble)
pvalthr <- pvalthrs[1]
# Set up parameters and directories
param <- paste0(gwas, qc, "_p=", pvalthrs[1]) # Set parameters for this test case
dir.create(paste0(work_dir, param, "/"), recursive = TRUE)

#===========================Read Exposure data for roi 1==============================
roi <- 1
exposure <- read.table(paste0(pheno_path, "scfc_sd_harm2_fam_roi", roi, ".phen"), header = FALSE)
names(exposure)[1:3] <- c("fid", "iid", "exposure")

df_out_cov_exp <- left_join(df_out_cov, exposure, by = c("fid", "iid"))

#===========================Read SNP data===================================
ct_pvalthr_path <- paste0(ct_path, "p=", pvalthrs[1], "/") 
if (!file.exists(paste0(ct_pvalthr_path, 'roi', roi, '.', "_p=", pvalthr, "_r2=", r2, ".txt"))) {
  cat(paste0("\n\nNo SNP to use for roi ", roi, "\n"))
} else {
  clumped_roi <- read.table(paste0(ct_pvalthr_path, 'roi', roi, '.', "_p=", pvalthr, "_r2=", r2, ".txt"), header = TRUE) %>% distinct()
  num_snps <- nrow(clumped_roi)
  cat(paste0("\n\n###################Performing 2SRI for roi ", roi, "; number of SNPs: ", num_snps, "; for pvalthr:", pvalthr, "########################\n\n"))
}

#=======================Filter SNPs Using PLINK and Prepare Data=======================
dir.create(paste0(work_dir, param, "/iv_bfile_c+t/"), recursive = FALSE)
write.table(data.frame(clumped_roi$SNP), paste0(work_dir, param, "/iv_bfile_c+t/snp_id_roi", roi, ".txt"), col.names = FALSE, row.names = FALSE, quote = FALSE, sep = "\t")

# use big bfile here because the unrelated sample always gives error
system(paste0(tool_path, "plink --bfile ", "/Users/grc8mu/Desktop/DS/ABCD_data/ABCD_bfile/bfile_for_gwas_comparison/ABCD_all",
              " --extract ", paste0(work_dir, param, "/iv_bfile_c+t/snp_id_roi", roi, ".txt"),
              " --make-bed --out ", work_dir, param, "/iv_bfile_c+t/iv_bfile_roi", roi),
       intern = FALSE)

# Read bfiles and get them ready
bfile <- read.plink(paste0(work_dir, param, "/iv_bfile_c+t/iv_bfile_roi", roi, ".bed"), 
                    paste0(work_dir, param, "/iv_bfile_c+t/iv_bfile_roi", roi, ".bim"), 
                    paste0(work_dir, param, "/iv_bfile_c+t/iv_bfile_roi", roi, ".fam"))
sub_matrix <- bfile$genotypes
SNPs <- as.data.frame(as.matrix(sub_matrix, type = "numeric"))
SNPs <- tibble::rownames_to_column(SNPs, "iid")

#========================Merge all data=====================================
df_all <- left_join(df_out_cov_exp, SNPs, by = "iid")
snp_names <- names(df_all)[10:ncol(df_all)]
df_all[snp_names] <- lapply(df_all[snp_names], function(x) as.numeric(as.character(x)) - 1)
df_all <- df_all %>%
  filter(outcome %in% c(0, 1)) %>% # Only keep binary outcome values (0 or 1)
  filter(!if_any(everything(), is.na))

#===========================2SRI Method===========================
# Stage 1: Linear regression of exposure on SNPs and covariates to obtain residuals
stage1 <- lm(exposure ~ . - outcome, data = df_all)
df_all$residuals_stage1 <- residuals(stage1)

# Stage 2: Logistic regression on outcome with exposure, residuals, and covariates
stage2 <- glm(outcome ~ exposure + residuals_stage1 + sex + interview_age + ethn + race, 
              family = binomial(link = "logit"), data = df_all)

# Extract coefficient, standard error, and p-value for the exposure variable
stage2_summary <- summary(stage2)
iv_coef <- stage2_summary$coefficients["exposure", "Estimate"]
iv_stderror <- stage2_summary$coefficients["exposure", "Std. Error"]
iv_pvalue <- stage2_summary$coefficients["exposure", "Pr(>|z|)"]
iv_z <- stage2_summary$coefficients["exposure", "z value"]

# Print results for verification
results_df <- data.frame(
  roi = roi,
  ROI = mmp_subcor[roi],
  IV_Coefficient = iv_coef,
  IV_StdError = iv_stderror,
  IV_Z = iv_z,
  IV_P_Value = iv_pvalue,
  Num_snps = num_snps,
  stringsAsFactors = FALSE
)
print(results_df)
```

```{r}
# Load necessary libraries for parallel computing
library(doParallel)
library(foreach)
library(dplyr)
library(tibble)

# Set up parallel backend
num_cores <- detectCores() - 1
cl <- makeCluster(num_cores)
registerDoParallel(cl)

############################## Compute 2SRI for Binary Outcome #####################################
for (pvalthr in pvalthrs) {
  param <- paste0(gwas, qc, "_p=", pvalthr) # Set parameters
  dir.create(paste0(work_dir, param, "/"), recursive = TRUE)
  
  # Create a directory to save individual regression summaries
  regression_summary_dir <- paste0(work_dir, param, "/regression_summaries/")
  dir.create(regression_summary_dir, recursive = TRUE)

  # Parallel foreach loop over roi
  results <- foreach(roi = 1:379, .packages = c("dplyr", "tibble", "data.table", "snpStats")) %dopar% {
    tryCatch({
      #=========================== Read Exposure Data ===============================
      exposure <- read.table(paste0(pheno_path, "scfc_sd_harm2_fam_roi", roi, ".phen"), header = FALSE)
      names(exposure)[1:3] <- c("fid", "iid", "exposure")
      
      df_out_cov_exp <- left_join(df_out_cov, exposure, by = c("fid", "iid"))
      
      #=========================== Read SNP Data ===================================
      ct_pvalthr_path <- paste0(ct_path, "p=", pvalthr, "/") 
      if (!file.exists(paste0(ct_pvalthr_path, 'roi', roi, '.', "_p=", pvalthr, "_r2=", r2, ".txt"))) {
        cat(paste0("\n\nNo SNP to use for roi ", roi, "\n"))
        return(NULL)
      } else {
        clumped_roi <- read.table(paste0(ct_pvalthr_path, 'roi', roi, '.', "_p=", pvalthr, "_r2=", r2, ".txt"), header = TRUE) %>% distinct()
        num_snps <- nrow(clumped_roi)
      }
      
      #======================= Filter SNPs Using PLINK and Prepare Data =======================
      dir.create(paste0(work_dir, param, "/iv_bfile_c+t/"), recursive = FALSE)
      write.table(data.frame(clumped_roi$SNP), paste0(work_dir, param, "/iv_bfile_c+t/snp_id_roi", roi, ".txt"), row.names = FALSE, quote = FALSE, sep = "\t")
      # use big bfile here because the unrelated sample always gives error
      system(paste0(tool_path, "plink --bfile ", "/Users/grc8mu/Desktop/DS/ABCD_data/ABCD_bfile/bfile_for_gwas_comparison/ABCD_all",
                    " --extract ", paste0(work_dir, param, "/iv_bfile_c+t/snp_id_roi", roi, ".txt"),
                    " --make-bed --out ", work_dir, param, "/iv_bfile_c+t/iv_bfile_roi", roi),
             intern = FALSE)
      
      bfile <- read.plink(paste0(work_dir, param, "/iv_bfile_c+t/iv_bfile_roi", roi, ".bed"), 
                          paste0(work_dir, param, "/iv_bfile_c+t/iv_bfile_roi", roi, ".bim"), 
                          paste0(work_dir, param, "/iv_bfile_c+t/iv_bfile_roi", roi, ".fam"))
      sub_matrix <- bfile$genotypes
      SNPs <- as.data.frame(as.matrix(sub_matrix, type = "numeric"))
      SNPs <- tibble::rownames_to_column(SNPs, "iid")
      
      #======================== Merge All Data =====================================
      df_all <- left_join(df_out_cov_exp, SNPs, by = "iid")
      snp_names <- names(df_all)[10:ncol(df_all)]
      df_all[snp_names] <- lapply(df_all[snp_names], function(x) as.numeric(as.character(x)) - 1)
      df_all <- df_all %>%
        filter(outcome %in% c(0, 1)) %>% # Only keep binary outcome values (0 or 1)
        filter(!if_any(everything(), is.na))
      
      #=========================== 2SRI Method ===========================
      # Stage 1: Linear regression of exposure on SNPs and covariates to obtain residuals
      stage1 <- lm(exposure ~ . - outcome, data = df_all)
      df_all$residuals_stage1 <- residuals(stage1)
      
      # Stage 2: Logistic regression on outcome with exposure, residuals, and covariates
      stage2 <- glm(outcome ~ exposure + residuals_stage1 + sex + interview_age + ethn + race, 
                    family = binomial(link = "logit"), data = df_all)
      
      # Save the full summary of stage2 to a text file
      summary_file <- paste0(regression_summary_dir, "regression_summary_roi", roi, ".txt")
      capture.output(summary(stage2), file = summary_file)

      # Extract coefficient, standard error, and p-value for the exposure variable
      stage2_summary <- summary(stage2)
      iv_coef <- stage2_summary$coefficients["exposure", "Estimate"]
      iv_stderror <- stage2_summary$coefficients["exposure", "Std. Error"]
      iv_pvalue <- stage2_summary$coefficients["exposure", "Pr(>|z|)"]
      iv_z <- stage2_summary$coefficients["exposure", "z value"]
      
      # Return results for this ROI
      data.frame(
        roi = roi,
        ROI = mmp_subcor[roi],
        IV_Coefficient = iv_coef,
        IV_StdError = iv_stderror,
        IV_Z = iv_z,
        IV_P_Value = iv_pvalue,
        Num_snps = num_snps,
        stringsAsFactors = FALSE
      )
      
    }, error = function(e) {
      return(NULL)  # Return NULL if any error occurs for this ROI
    })
  }
  
  # Stop the parallel backend after finishing the roi loop
  stopCluster(cl)
  
  # Combine results from all ROIs in this pvalthr iteration
  results_df <- do.call(rbind, results)
  
  # Save results for this pvalthr value
  write.csv(results_df, paste0(work_dir, "2SRI_results_", param, ".csv"))
  cat(paste0("\n\n################### Successfully saved 2SRI results for all ROIs; pvalthr:", pvalthr, " ########################\n\n"))
}

```

```{r}

```
