---
title: "C+T_1009"
author: "Chengyan Ji"
date: "2024-10-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**10/09: This is C+T for fastGWA and GWASPlink2.0 with only sex as covariate, phenotype: trans_harm2, QCed data**
**10/09: This task uses the new directory system**
**10/09: Add readme and SNPcounts**
**10/09: Structure: bfile_by_chr --> Thresholding(pvalthr) --> save results(pvalthr) --> clumping(pvalthr)**
**10/09: Will introduce duplicates if all content not removed before running**
**10/09: Current readme in C+Ted folder will only show ROIs with no significant SNPs after C+T, but not show which ROI has no GWAS results, please original GWAS folder readme**
**02/15: Now changed to Doing C+T for new 2 additional sensitivity analyses**

# ```{r}
#     #---------Save GWAS results-----------------------------------------------
#     #+++++++++Set save directory++++++++++++++++++++++++++++++++++++++++++++++
#     save_dir <- paste0(work_dir, "gwas_results_csv/")
#     if (!dir.exists(save_dir)) { dir.create(save_dir, recursive = F) }
#     #+++++++++Create readme+++++++++++++++++++++++++++++++++++++++++++++++++++
#     readme_path <- paste0(save_dir, "readme.txt")
#     readme_conn <- file(readme_path, "w")
#     writeLines(paste0("GWAS using ", method, qc, unrel, "\n\n"), readme_conn)
#     command <- paste0(tool_path, "plink2 --bfile ", bfile, " ",
#                           "--pheno ", paste0(pheno_path, "roi_", "adhd", ".phen"), " ",
#                           "--covar ", covar_sex, " ",
#                           "--glm no-x-sex hide-covar ",  # Added hide-covar to avoid covariate effect lines in the output
#                           "--covar-variance-standardize ",
#                           "--out ", paste0(work_dir, method, qc, unrel, "_roi_", "adhd"))
#     writeLines(paste0("Commands run: ", command, "\n\n"), readme_conn)
#     start_time <- Sys.time()
#     missing <- 0
#     #+++++++++Create SNP counts+++++++++++++++++++++++++++++++++++++++++++++++
#     count_path <- paste0(save_dir, "SNP_counts.txt")
#     count_conn <- file(count_path, "w")
#     writeLines(paste0("SNPs P<5e-08 for GWAS using ", method, qc, unrel, "\n\n"), count_conn)
#     #---------Read results for rois-------------------------------------------
#     cat(paste0("\n^^^^^^^^^^^^Reading GWAS results: ", method, qc, unrel, "^^^^^^^^^^^^\n"))
#     num_cores <- detectCores() - 1
#     cl <- makeCluster(num_cores)
#     registerDoParallel(cl)
#     # parallel read gwas results
#     parallel_results <- foreach(roi = rois, .packages = c("dplyr")) %dopar% {
#       library(dplyr)
#       tryCatch({
#         gwas_result_path <- paste0(work_dir, method, qc, unrel, "_roi_", roi,  ".PHENO1.glm.linear")
#         if (file.exists(gwas_result_path)) {
#           gwas_result <- read.table(gwas_result_path, header = F, sep = "\t")
#           colnames(gwas_result) <- c("#CHROM", "POS", "SNP", "REF", "ALT", "PROVISIONAL_REF?", "A1", "OMITTED", "A1_FREQ", "TEST", "OBS_CT", "BETA", "SE", "T_STAT", "P", "ERRCODE")
#           write.csv(gwas_result, paste0(save_dir, method, qc, unrel, "_roi_", roi,  ".csv"), row.names = FALSE, quote = FALSE)
#           sig_snp_count <- nrow(gwas_result %>% filter(P < 5e-08))
#           return(list(roi = roi, missing = FALSE, snp_count = sig_snp_count))
#         } else {
#           return(list(roi = roi, missing = TRUE, snp_count = NA))
#         }}, error = function(e) {
#           return(list(roi = roi, error = paste("Error:", e$message), missing = TRUE, snp_count = NA))
#       })
#     }
#     stopCluster(cl)
#     cat(paste0("^^^^^^^^^^^^Finished Reading GWAS results: ", method, qc, unrel, "^^^^^^^^^^^^\n\n"))
# ```

```{r}
library(optparse)
library(parallel)
library(readr)
library(bigreadr)
library(bigsnpr)
library(data.table)
library(dplyr)
library(metafor)

### Define directories==========================================================
in_dir <- "/Users/grc8mu/Desktop/DS/20250215_GWAS/"
directory <- "/Users/grc8mu/Desktop/DS/20250215_MR/"
plink_path <- paste0("/Users/grc8mu/Desktop/DS/Tools/", "plink")
bfile_path <- paste0("/Users/grc8mu/Desktop/DS/ABCD_data/", "ABCD_bfile/bfile_for_gwas_comparison/")

### Set Parameters==============================================================
# Input:
NCORES = 1 # Number of cores used for training lassosum2 models under different tuning parameter settings.
# Parameters for the Clumping step
kb = 500 # SNPs within 500kb of the index SNP are considered for clumping
p.ldclump = 0.5 # LD p-value threshold for a SNP to be included as an index SNP
pvalthrs = c(5e-08) #c(5e-06, 5e-07, 5e-08) # p-value threshold for thresholding
r2 = 0.001 # SNPs having r2 higher than 0.1 with the index SNPs will be removed # optional: c(0.1,0.2,0.4,0.6,0.8)

trait_name <- "adhd" ## This is not used
method <- 'method' ## I AM NOT SURE WHAT THIS IS ## there was a variable called "method" but never used in the original code
ite <- 1 ## I AM NOT SURE WHAT THIS IS

#========================================================================================================================  
#========================================================================================================================  

QCs <- c("_qc") # qc and no qc: "_noqc"
unrels <- c("_unrelated") #c("_unrelated") # all obs and unrelated obs
harms <- c("_sd_harm2") # harm2 and fisher+harm2
methods <- c("gwasplink20_nocov") # c("gwasplink20_covsex", "")
rois <- (1:379)

################################################### For Loop 1 Begins ###################################################
for (qc in QCs) {
  for (unrel in unrels) {
    #-----------get bfile---------------------------------------------------------
    bfile <- paste0(bfile_path, "scfc_all", qc, unrel)
    for (harm in harms) {
      for (method in methods) {
        #------------------Get directory for storing GWAS results---------------
        gwas_dir <- paste0(in_dir, method, qc, unrel, harm, "/")
        #------------------Set up directory to save MR results------------------
        work_dir <- paste0(directory, method, qc, unrel, harm, "_MR/")
        if (!dir.exists(work_dir)) { dir.create(work_dir, recursive = F) }
        #=============Create directories for C+T========================================
        #-------------1st level directories---------------------------------------------
        # 1.1: for storing bfile by chr, same for all pvalthr
        if (!dir.exists(paste0(work_dir, "bfile_by_chr/"))) { dir.create(paste0(work_dir, "bfile_by_chr/"), recursive = F) }
        # 1.2: for storing C+T results (contain parallel Thresholding, Clumping and C+T directories)
        ct_results_path <- paste0(work_dir, "C+T/") 
        if (!dir.exists(ct_results_path)) { dir.create(ct_results_path, recursive = F) }
        # 1.3: beneath C+T/: Thresholding, Clumping and C+T
        thresh_path <- paste0(work_dir, "C+T/Thresholding/") # 1.3.1: Thresholding results
        if (!dir.exists(thresh_path)) { dir.create(thresh_path, recursive = F) }
        clumping_path <- paste0(work_dir, "C+T/Clumping/")   # 1.3.2: Clumping results
        if (!dir.exists(clumping_path)) { dir.create(clumping_path, recursive = F) }
        ct_path <- paste0(work_dir, "C+T/C+Ted_", method, qc, unrel, harm, "/")            # 1.3.3: Processed C+T results containing SNP and test results
        if (!dir.exists(ct_path)) { dir.create(ct_path, recursive = F) }
        
        ## I. Break geno files by CHRs (ABCD actually comes separated but QC combined them) and store to "bfile_by_chr/"
        for (chr in 1:22) {
          output_path <- paste0('"', work_dir, "bfile_by_chr/scfc_all", qc, unrel, "_chr", chr, '"')
          command <- paste(plink_path, "--bfile", bfile, "--chr", chr, "--make-bed --out", output_path)
          system(command, intern=TRUE)
        }
        for (roi in rois) {
          #==============================read GWAS results==============================
          gwas_path <- paste0(gwas_dir, method, qc, unrel, "_scfc", harm, "_fam_roi", roi,  ".PHENO1.glm.linear")
          if (file.exists(gwas_path)) {
            gwas_roi <- read.table(gwas_path, header = F, sep = "\t")
            colnames(gwas_roi) <- c("#CHROM", "POS", "SNP", "REF", "ALT", "PROVISIONAL_REF?", "A1", "OMITTED", "A1_FREQ", "TEST", "OBS_CT", "BETA", "SE", "T_STAT", "P", "ERRCODE") # The chrome column name keeps changing names i don't know why
            gwas_roi <- gwas_roi %>% rename(CHR = `#CHROM`, REF_plink = REF, ALT_plink = ALT, PROVISIONAL_REF_plink = `PROVISIONAL_REF?`, A1_plink = A1, OMITTED_plink = OMITTED, AF1_plink = A1_FREQ, N = OBS_CT) %>%
              mutate(A1_fastgwa = NA, A2_fastgwa = NA, AF1_fastgwa = NA) %>% # Add empty columns for FastGWA-specific fields
              select(CHR, SNP, POS, REF_plink, ALT_plink, PROVISIONAL_REF_plink, A1_plink, OMITTED_plink, AF1_plink, A1_fastgwa, A2_fastgwa, AF1_fastgwa, N, BETA, SE, P) # only keep necessary columns (both plink and fastgwa columns are kept)
            
            sig_snp_count <- nrow(gwas_roi %>% filter(P < 5e-08))
            print(paste0("roi",roi,": significant SNPs: ", sig_snp_count))
          } else {
            cat("No GWAS results available for roi:", roi, "skipping current roi...")
            next
          }
          #-----------------------------------------------------------------------------
          #### IV Selection (using exposure: scfc)######################################
          ### Run T+C (Thresholding first and Clumping next)============================
          for (pvalthr in pvalthrs) {
            # -----for inspection purpose, output thresholding results to local---------
            gwas_roi.thresh <- gwas_roi[gwas_roi$P <= pvalthr,]
            thresh_count_path <- paste0(thresh_path, "threshold_count/", method, qc, unrel, "_", pvalthr, "/")
            if (!dir.exists(thresh_count_path)) { dir.create(thresh_count_path, recursive = TRUE) }
            write.table(gwas_roi.thresh, paste0(thresh_count_path, "gwas_thresh_roi",roi,".txt"), row.names = F, col.names = T, quote = F)
            readme_path <- paste0(thresh_count_path, "readme.txt")
            readme_conn <- file(readme_path, "a")
            writeLines(paste0("roi", roi, " after thresholding: ", nrow(gwas_roi.thresh)), readme_conn)
            close(readme_conn)
            
            ## ---------------------2nd level Directories-------------------------------
            ## 2.1 Thresholding
            thresh_idlist_path <- paste0(thresh_path, "thr_idlists/")                   # 2.1.1 for storing SNP id lists for plink to subset bfiles
            if (!dir.exists(thresh_idlist_path)) { dir.create(thresh_idlist_path, recursive = F) }
            thresh_bfile_by_chr_path <- paste0(thresh_path, "thr_bfile_by_chr/")        # 2.1.2 for storing bfile by chr AFTER thresholding (for clumping)
            if (!dir.exists(thresh_bfile_by_chr_path)) { dir.create(thresh_bfile_by_chr_path, recursive = F) }
            thresh_gwas_path <- paste0(thresh_path, "thr_gwas/")                           # 2.1.3 for storing GWAS results filtered AFTER thresholding (for clumping) 
            if (!dir.exists(thresh_gwas_path)) { dir.create(thresh_gwas_path, recursive = F) }
            
            ## 2.2 Clumping
            clump_clumped_path <- paste0(clumping_path, "clumped/")                     # 2.2.1 for storing raw clumped results, by chr
            if (!dir.exists(clump_clumped_path)) { dir.create(clump_clumped_path, recursive = F) }
            
            ## 2.3 C+T does not need additional sub-directories
            
            ## --------------------3rd level Directories (pvalthr)----------------------
            # create directories for thresholding p-values (pvalthr)
            # 2.1.1 thresholding directories
            thresh_idlist_pvalthr_path <- paste0(thresh_idlist_path, "idlist_p=", pvalthr, "/")                    # 2.1.1.1 for storing SNP id lists for current pvalthr
            if (!dir.exists(thresh_idlist_pvalthr_path)) { dir.create(thresh_idlist_pvalthr_path, recursive = F) }
            thresh_bfile_by_chr_pvalthr_path <- paste0(thresh_bfile_by_chr_path, "bfile_by_chr_p=", pvalthr, "/")  # 2.1.2.1 for storing bfiles for current pvalthr
            if (!dir.exists(thresh_bfile_by_chr_pvalthr_path)) { dir.create(thresh_bfile_by_chr_pvalthr_path, recursive = F) }
            thresh_gwas_pvalthr_path <- paste0(thresh_gwas_path, "gwas_p=", pvalthr, "/")                          # 2.1.3.1 for storing GWAS results for current pvalthr
            if (!dir.exists(thresh_gwas_pvalthr_path)) { dir.create(thresh_gwas_pvalthr_path, recursive = F) }
            
            # 2.2.1 clumping directories
            clump_clumped_pvalthr_path <- paste0(clump_clumped_path, "clumped_p=", pvalthr, "/")                 # 2.2.1.1 for storing raw clumped results for current pvalthr
            if (!dir.exists(clump_clumped_pvalthr_path)) { dir.create(clump_clumped_pvalthr_path, recursive = F) }
            
            # 2.3.1 C+T directories
            ct_pvalthr_path <- paste0(ct_path, "p=", pvalthr, "/")                                                 # 2.3.1.1 for storing C+T results for current pvalthr 
            if (!dir.exists(ct_pvalthr_path)) { dir.create(ct_pvalthr_path, recursive = F) }
            ct_final_path <- paste0(ct_pvalthr_path, 'roi', roi, '.', "_p=", pvalthr, "_r2=", r2, ".txt")          # 2.3.1.2 txt file for storing final C+T SNPs, used if clumping is successful
        
            #---------------------------------------------------------------------------
            for (chr in 1:22){
        
              sum.chrspecific = gwas_roi[gwas_roi$CHR == chr,]
              # --------------------- Step 2.2: Run C+T --------------------------------
              set.seed(2023)
              
              ## --------------------- Thresholding (T) --------------------------------
              # filter SNPs by p-value
              sum.data <- sum.chrspecific
              sum.data <- sum.data[sum.data$P <= pvalthr,]
              # writes list of filtered SNP id
              snp_id_list <- paste0(thresh_idlist_pvalthr_path, "idlist_roi",roi,'_chr',chr,'_pvalthr',pvalthr,".txt") #这个filtered指的是thresholding
              write.table(sum.data[,'SNP'], snp_id_list, quote = F, col.names = F, row.names = F)
              
              # write filtered SNPs bfile back to SNP list using PLINK1.9
              system(paste0(plink_path, " --bfile ", work_dir, "bfile_by_chr/scfc_all", qc, unrel, "_chr", chr,
                            " --extract ", snp_id_list,
                            " --make-bed --out ", thresh_bfile_by_chr_pvalthr_path, "scfc_all", qc, unrel, "_thr","_roi",roi,'_chr',chr,'_pvalthr',pvalthr), # filtered snps by chr
                     intern = T)
              
              # write the threshold GWAS summary with SNP and P-value to local (to be used by clumping)
              sumstats_input <- sum.data[,c('SNP','P')]
              fwrite(sumstats_input, file=paste0(thresh_gwas_pvalthr_path,'gwas_roi',roi,'_chr',chr,'_pvalthr',pvalthr,'.txt'),row.names = F, quote = F, sep=' ')
              
              cat('\nTHRESHOLDING FINISHED roi:',roi,' chr:',chr," pvalthr:",pvalthr)
              
              ## --------------------- LD Clumping (C) ---------------------
              # outputfilename
              clumpedfilename <- paste0("roi",roi,'_chr',chr,"_clumped") # C+T files naming: removed "adhd" in the name, removed "ite", put "roi" before "chr"
              # run clumping on plink
              ldclumpcode <- paste0(plink_path, 
                                    ' --bfile ',thresh_bfile_by_chr_pvalthr_path,"scfc_all",qc,unrel,"_thr","_roi",roi,'_chr',chr,'_pvalthr',pvalthr,
                                    ' --clump ',thresh_gwas_pvalthr_path,'gwas_roi',roi,'_chr',chr,'_pvalthr',pvalthr,'.txt',
                                    ' --clump-p1 ',p.ldclump,
                                    ' --clump-r2 ',r2,
                                    ' --clump-kb ',kb,
                                    ' --threads 1',
                                    # ' --silent',
                                    ' --out ',clump_clumped_pvalthr_path,clumpedfilename)
              system(ldclumpcode, intern = T)
              cat('\nCLUMPING FINISHED roi:',roi,' chr:',chr," pvalthr:",pvalthr)
              
              ##===================== read clumped files================================
              # First confirm that there is valid clumped results
              if (!file.exists(paste0(clump_clumped_pvalthr_path,clumpedfilename,'.clumped'))) {
                cat('\nNO CLUMPING RESULTS AVAILABLE for roi:',roi,' chr:',chr," pvalthr:",pvalthr)
                next
              }
              LD <- bigreadr::fread2(paste0(clump_clumped_pvalthr_path,clumpedfilename,'.clumped'))
              clump.snp <- LD[,3,drop=F]
              prs.all <- left_join(clump.snp,sum.data,by="SNP")
              
              prs.file = prs.all[prs.all$P <= pvalthr,] # USELESS?
              # -------------------------- Append the SNPs by chr ----------------------
              if (file.exists(ct_final_path)) {
                write.table(prs.file, file = ct_final_path, append = TRUE, col.names = FALSE, row.names = F, quote = F)
              } else {
                write.table(prs.file, file = ct_final_path, append = FALSE, col.names = TRUE, row.names = F, quote = F)
              }
              cat('\nC+T DONE for roi:',roi,' chr:',chr," pvalthr:", pvalthr)
            }
            # ------for inspection purpose, output C+T counts results to local----------
            readme_path <- paste0(ct_pvalthr_path, "readme.txt")
            readme_conn <- file(readme_path, "a")
            if (file.exists(ct_final_path)) {
              ct.count <- read.table(ct_final_path, header = T)
              writeLines(paste0("roi", roi, " after C+T: ", nrow(ct.count)), readme_conn)
            } else {
              writeLines(paste0("roi", roi, " after C+T: ", "No SNPs pass C+T"), readme_conn)
            }
            close(readme_conn)
          }
        ####
        }
      }
    }
  }
}
```

```{r}
#========================================================================================================================  
#========================================================================================================================  

QCs <- c("_qc") # qc and no qc: "_noqc"
unrels <- c("_unrelated") #c("_unrelated") # all obs and unrelated obs
harms <- c("_sd") # harm2 and fisher+harm2
methods <- c("gwasplink20_covsex") # c("gwasplink20_covsex", "")
rois <- (1:379)

################################################### For Loop 1 Begins ###################################################
for (qc in QCs) {
  for (unrel in unrels) {
    #-----------get bfile---------------------------------------------------------
    bfile <- paste0(bfile_path, "scfc_all", qc, unrel)
    for (harm in harms) {
      for (method in methods) {
        #------------------Get directory for storing GWAS results---------------
        gwas_dir <- paste0(in_dir, method, qc, unrel, harm, "/")
        #------------------Set up directory to save MR results------------------
        work_dir <- paste0(directory, method, qc, unrel, harm, "_MR/")
        if (!dir.exists(work_dir)) { dir.create(work_dir, recursive = F) }
        #=============Create directories for C+T========================================
        #-------------1st level directories---------------------------------------------
        # 1.1: for storing bfile by chr, same for all pvalthr
        if (!dir.exists(paste0(work_dir, "bfile_by_chr/"))) { dir.create(paste0(work_dir, "bfile_by_chr/"), recursive = F) }
        # 1.2: for storing C+T results (contain parallel Thresholding, Clumping and C+T directories)
        ct_results_path <- paste0(work_dir, "C+T/") 
        if (!dir.exists(ct_results_path)) { dir.create(ct_results_path, recursive = F) }
        # 1.3: beneath C+T/: Thresholding, Clumping and C+T
        thresh_path <- paste0(work_dir, "C+T/Thresholding/") # 1.3.1: Thresholding results
        if (!dir.exists(thresh_path)) { dir.create(thresh_path, recursive = F) }
        clumping_path <- paste0(work_dir, "C+T/Clumping/")   # 1.3.2: Clumping results
        if (!dir.exists(clumping_path)) { dir.create(clumping_path, recursive = F) }
        ct_path <- paste0(work_dir, "C+T/C+Ted_", method, qc, unrel, harm, "/")            # 1.3.3: Processed C+T results containing SNP and test results
        if (!dir.exists(ct_path)) { dir.create(ct_path, recursive = F) }
        
        ## I. Break geno files by CHRs (ABCD actually comes separated but QC combined them) and store to "bfile_by_chr/"
        for (chr in 1:22) {
          output_path <- paste0('"', work_dir, "bfile_by_chr/scfc_all", qc, unrel, "_chr", chr, '"')
          command <- paste(plink_path, "--bfile", bfile, "--chr", chr, "--make-bed --out", output_path)
          system(command, intern=TRUE)
        }
        for (roi in rois) {
          #==============================read GWAS results==============================
          gwas_path <- paste0(gwas_dir, method, qc, unrel, "_scfc", harm, "_fam_roi", roi,  ".PHENO1.glm.linear")
          if (file.exists(gwas_path)) {
            gwas_roi <- read.table(gwas_path, header = F, sep = "\t")
            colnames(gwas_roi) <- c("#CHROM", "POS", "SNP", "REF", "ALT", "PROVISIONAL_REF?", "A1", "OMITTED", "A1_FREQ", "TEST", "OBS_CT", "BETA", "SE", "T_STAT", "P", "ERRCODE") # The chrome column name keeps changing names i don't know why
            gwas_roi <- gwas_roi %>% rename(CHR = `#CHROM`, REF_plink = REF, ALT_plink = ALT, PROVISIONAL_REF_plink = `PROVISIONAL_REF?`, A1_plink = A1, OMITTED_plink = OMITTED, AF1_plink = A1_FREQ, N = OBS_CT) %>%
              mutate(A1_fastgwa = NA, A2_fastgwa = NA, AF1_fastgwa = NA) %>% # Add empty columns for FastGWA-specific fields
              select(CHR, SNP, POS, REF_plink, ALT_plink, PROVISIONAL_REF_plink, A1_plink, OMITTED_plink, AF1_plink, A1_fastgwa, A2_fastgwa, AF1_fastgwa, N, BETA, SE, P) # only keep necessary columns (both plink and fastgwa columns are kept)
            
            sig_snp_count <- nrow(gwas_roi %>% filter(P < 5e-08))
            print(paste0("roi",roi,": significant SNPs: ", sig_snp_count))
          } else {
            cat("No GWAS results available for roi:", roi, "skipping current roi...")
            next
          }
          #-----------------------------------------------------------------------------
          #### IV Selection (using exposure: scfc)######################################
          ### Run T+C (Thresholding first and Clumping next)============================
          for (pvalthr in pvalthrs) {
            # -----for inspection purpose, output thresholding results to local---------
            gwas_roi.thresh <- gwas_roi[gwas_roi$P <= pvalthr,]
            thresh_count_path <- paste0(thresh_path, "threshold_count/", method, qc, unrel, "_", pvalthr, "/")
            if (!dir.exists(thresh_count_path)) { dir.create(thresh_count_path, recursive = TRUE) }
            write.table(gwas_roi.thresh, paste0(thresh_count_path, "gwas_thresh_roi",roi,".txt"), row.names = F, col.names = T, quote = F)
            readme_path <- paste0(thresh_count_path, "readme.txt")
            readme_conn <- file(readme_path, "a")
            writeLines(paste0("roi", roi, " after thresholding: ", nrow(gwas_roi.thresh)), readme_conn)
            close(readme_conn)
            
            ## ---------------------2nd level Directories-------------------------------
            ## 2.1 Thresholding
            thresh_idlist_path <- paste0(thresh_path, "thr_idlists/")                   # 2.1.1 for storing SNP id lists for plink to subset bfiles
            if (!dir.exists(thresh_idlist_path)) { dir.create(thresh_idlist_path, recursive = F) }
            thresh_bfile_by_chr_path <- paste0(thresh_path, "thr_bfile_by_chr/")        # 2.1.2 for storing bfile by chr AFTER thresholding (for clumping)
            if (!dir.exists(thresh_bfile_by_chr_path)) { dir.create(thresh_bfile_by_chr_path, recursive = F) }
            thresh_gwas_path <- paste0(thresh_path, "thr_gwas/")                           # 2.1.3 for storing GWAS results filtered AFTER thresholding (for clumping) 
            if (!dir.exists(thresh_gwas_path)) { dir.create(thresh_gwas_path, recursive = F) }
            
            ## 2.2 Clumping
            clump_clumped_path <- paste0(clumping_path, "clumped/")                     # 2.2.1 for storing raw clumped results, by chr
            if (!dir.exists(clump_clumped_path)) { dir.create(clump_clumped_path, recursive = F) }
            
            ## 2.3 C+T does not need additional sub-directories
            
            ## --------------------3rd level Directories (pvalthr)----------------------
            # create directories for thresholding p-values (pvalthr)
            # 2.1.1 thresholding directories
            thresh_idlist_pvalthr_path <- paste0(thresh_idlist_path, "idlist_p=", pvalthr, "/")                    # 2.1.1.1 for storing SNP id lists for current pvalthr
            if (!dir.exists(thresh_idlist_pvalthr_path)) { dir.create(thresh_idlist_pvalthr_path, recursive = F) }
            thresh_bfile_by_chr_pvalthr_path <- paste0(thresh_bfile_by_chr_path, "bfile_by_chr_p=", pvalthr, "/")  # 2.1.2.1 for storing bfiles for current pvalthr
            if (!dir.exists(thresh_bfile_by_chr_pvalthr_path)) { dir.create(thresh_bfile_by_chr_pvalthr_path, recursive = F) }
            thresh_gwas_pvalthr_path <- paste0(thresh_gwas_path, "gwas_p=", pvalthr, "/")                          # 2.1.3.1 for storing GWAS results for current pvalthr
            if (!dir.exists(thresh_gwas_pvalthr_path)) { dir.create(thresh_gwas_pvalthr_path, recursive = F) }
            
            # 2.2.1 clumping directories
            clump_clumped_pvalthr_path <- paste0(clump_clumped_path, "clumped_p=", pvalthr, "/")                 # 2.2.1.1 for storing raw clumped results for current pvalthr
            if (!dir.exists(clump_clumped_pvalthr_path)) { dir.create(clump_clumped_pvalthr_path, recursive = F) }
            
            # 2.3.1 C+T directories
            ct_pvalthr_path <- paste0(ct_path, "p=", pvalthr, "/")                                                 # 2.3.1.1 for storing C+T results for current pvalthr 
            if (!dir.exists(ct_pvalthr_path)) { dir.create(ct_pvalthr_path, recursive = F) }
            ct_final_path <- paste0(ct_pvalthr_path, 'roi', roi, '.', "_p=", pvalthr, "_r2=", r2, ".txt")          # 2.3.1.2 txt file for storing final C+T SNPs, used if clumping is successful
        
            #---------------------------------------------------------------------------
            for (chr in 1:22){
        
              sum.chrspecific = gwas_roi[gwas_roi$CHR == chr,]
              # --------------------- Step 2.2: Run C+T --------------------------------
              set.seed(2023)
              
              ## --------------------- Thresholding (T) --------------------------------
              # filter SNPs by p-value
              sum.data <- sum.chrspecific
              sum.data <- sum.data[sum.data$P <= pvalthr,]
              # writes list of filtered SNP id
              snp_id_list <- paste0(thresh_idlist_pvalthr_path, "idlist_roi",roi,'_chr',chr,'_pvalthr',pvalthr,".txt") #这个filtered指的是thresholding
              write.table(sum.data[,'SNP'], snp_id_list, quote = F, col.names = F, row.names = F)
              
              # write filtered SNPs bfile back to SNP list using PLINK1.9
              system(paste0(plink_path, " --bfile ", work_dir, "bfile_by_chr/scfc_all", qc, unrel, "_chr", chr,
                            " --extract ", snp_id_list,
                            " --make-bed --out ", thresh_bfile_by_chr_pvalthr_path, "scfc_all", qc, unrel, "_thr","_roi",roi,'_chr',chr,'_pvalthr',pvalthr), # filtered snps by chr
                     intern = T)
              
              # write the threshold GWAS summary with SNP and P-value to local (to be used by clumping)
              sumstats_input <- sum.data[,c('SNP','P')]
              fwrite(sumstats_input, file=paste0(thresh_gwas_pvalthr_path,'gwas_roi',roi,'_chr',chr,'_pvalthr',pvalthr,'.txt'),row.names = F, quote = F, sep=' ')
              
              cat('\nTHRESHOLDING FINISHED roi:',roi,' chr:',chr," pvalthr:",pvalthr)
              
              ## --------------------- LD Clumping (C) ---------------------
              # outputfilename
              clumpedfilename <- paste0("roi",roi,'_chr',chr,"_clumped") # C+T files naming: removed "adhd" in the name, removed "ite", put "roi" before "chr"
              # run clumping on plink
              ldclumpcode <- paste0(plink_path, 
                                    ' --bfile ',thresh_bfile_by_chr_pvalthr_path,"scfc_all",qc,unrel,"_thr","_roi",roi,'_chr',chr,'_pvalthr',pvalthr,
                                    ' --clump ',thresh_gwas_pvalthr_path,'gwas_roi',roi,'_chr',chr,'_pvalthr',pvalthr,'.txt',
                                    ' --clump-p1 ',p.ldclump,
                                    ' --clump-r2 ',r2,
                                    ' --clump-kb ',kb,
                                    ' --threads 1',
                                    # ' --silent',
                                    ' --out ',clump_clumped_pvalthr_path,clumpedfilename)
              system(ldclumpcode, intern = T)
              cat('\nCLUMPING FINISHED roi:',roi,' chr:',chr," pvalthr:",pvalthr)
              
              ##===================== read clumped files================================
              # First confirm that there is valid clumped results
              if (!file.exists(paste0(clump_clumped_pvalthr_path,clumpedfilename,'.clumped'))) {
                cat('\nNO CLUMPING RESULTS AVAILABLE for roi:',roi,' chr:',chr," pvalthr:",pvalthr)
                next
              }
              LD <- bigreadr::fread2(paste0(clump_clumped_pvalthr_path,clumpedfilename,'.clumped'))
              clump.snp <- LD[,3,drop=F]
              prs.all <- left_join(clump.snp,sum.data,by="SNP")
              
              prs.file = prs.all[prs.all$P <= pvalthr,] # USELESS?
              # -------------------------- Append the SNPs by chr ----------------------
              if (file.exists(ct_final_path)) {
                write.table(prs.file, file = ct_final_path, append = TRUE, col.names = FALSE, row.names = F, quote = F)
              } else {
                write.table(prs.file, file = ct_final_path, append = FALSE, col.names = TRUE, row.names = F, quote = F)
              }
              cat('\nC+T DONE for roi:',roi,' chr:',chr," pvalthr:", pvalthr)
            }
            # ------for inspection purpose, output C+T counts results to local----------
            readme_path <- paste0(ct_pvalthr_path, "readme.txt")
            readme_conn <- file(readme_path, "a")
            if (file.exists(ct_final_path)) {
              ct.count <- read.table(ct_final_path, header = T)
              writeLines(paste0("roi", roi, " after C+T: ", nrow(ct.count)), readme_conn)
            } else {
              writeLines(paste0("roi", roi, " after C+T: ", "No SNPs pass C+T"), readme_conn)
            }
            close(readme_conn)
          }
        ####
        }
      }
    }
  }
}
```

```{r}

```
