---
title: "gwas_unrelated_mac_standardized"
author: "Chengyan Ji"
date: "2024-09-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- **一个小插曲：上次跑的时候文件名字写错了，跑之前先跑一下下面的代码把名字改回来** -->
<!-- ```{r} -->
<!-- dir_path <- "phenotype_roi/" -->
<!-- files <- list.files(path = dir_path, pattern = "_covar", full.names = TRUE) -->
<!-- new_files <- gsub("_covar", "", files) -->
<!-- results <- file.rename(from = files, to = new_files) -->
<!-- ``` -->

**This is modification after 09/06 Meeting**
**09/20: I now run gwas for ALL ROIs**
**09/20: 2 GWAS slightly different, susepect becasue 5628 ids not same every time, not using phenotype and bfile from 0906**
**09/30: Redo GWAS using Plink2.0 on unrelated data and noqc data, with covariates**
**10/01: found mistake, did not remove qc so redo**

```{r}
#library(snpStats)
library(tidyr)
library(tibble)
library(dplyr)
#library(AER)
library(readxl)
library(ggplot2)
library(readr)
```

## **GWAS using PLINK2.0 (on unrelated data)**

Main modifications

- 1 individual per family
- Phenotype
  - fill NAs with 0
  - do Fisher's transformation
  - harmonize
  
- bfiles
  - do not remove NAs this time
  - NOT QCed

<!-- - Only do GWAS for ROIs with no fastGWA results -->
<!-- ### Need to get the ROIs with no fastGWA results -->

<!-- # ```{r} -->
<!-- # readme_path <- "/Users/kurt/Documents/Data_Science_Project/0906_fastGWA_standardized/gwas_results_0906/fastGWA_default_allcovar/fastGWA_default_allcovar_csv/readme.txt"  # Update this path to your actual file path -->
<!-- # readme_content <- readLines(readme_path) -->
<!-- # pattern <- "Missing file for ROI (\\d+):" -->
<!-- # missing <- regmatches(readme_content, gregexpr(pattern, readme_content)) -->
<!-- # missing <- sapply(missing, function(x) as.numeric(gsub(pattern, "\\1", x))) -->
<!-- # missing <- unlist(missing) -->
<!-- # missing <- missing[!is.na(missing)]  # Remove NA values that result from lines without matches -->
<!-- # ``` -->
  
### Get unrelated ids (one from each family) and create phenotype and covariates
```{r}
phenotype_temp <- read.table("phenotype_roi/scfc_sd_harm2_family_roi1.phen") %>% rename(fid=V1, iid=V2, phenotype=V3)
fid_iid_scfc <- phenotype_temp[,c(1,2)]
fid_iid_scfc_unrelated <- fid_iid_scfc %>%
  group_by(fid) %>%
  slice_sample(n = 1) %>%
  ungroup() %>%
  arrange(iid)

write.table(fid_iid_scfc_unrelated, paste0("bfile/fid_iid_scfc_unrelated.txt"), col.names = F, row.names = F, quote = F, sep = "\t")
# inspect, should be 5628(5487 after removing covar, but not here)
length(unique(read.table(paste0("bfile/fid_iid_scfc_unrelated.txt"))[,1]))

## get covariates
qcovar_age_unrelated <- read.table(paste0("covariates/qcovar_age.txt")) %>% rename(fid=V1, iid=V2) %>%
  inner_join(fid_iid_scfc_unrelated, by = c("fid", "iid"))
covar_sex_race_ethn_unrelated <- read.table(paste0("covariates/covar_sex_race_ethn.txt")) %>% rename(fid=V1, iid=V2) %>%
  inner_join(fid_iid_scfc_unrelated, by = c("fid", "iid"))
covar_all <- qcovar_age_unrelated %>%
  inner_join(covar_sex_race_ethn_unrelated, by = c("fid", "iid"))

## loop to get phenotype unrelated subset
for (i in 1:379) {
  phenotype_data <- read.table(paste0("phenotype_roi/scfc_sd_harm2_family_roi", i, ".phen")) %>% rename(fid=V1, iid=V2) %>%
    inner_join(fid_iid_scfc_unrelated, by = c("fid", "iid"))
  file_name <- paste0("phenotype_roi/scfc_unrelated_sd_harm2_family_roi", i, ".phen")
  write.table(phenotype_data, file = file_name, row.names = F, col.names = F, quote = F)
  # cat("File", file_name, "has been created.\n")
}

# Covariate files
write.table(qcovar_age_unrelated, paste0("covariates/qcovar_age.txt"), col.names = F, row.names = F, quote = F, sep = "\t")
write.table(covar_sex_race_ethn_unrelated, paste0("covariates/covar_sex_race_ethn.txt"), col.names = F, row.names = F, quote = F, sep = "\t")
write.table(covar_all, paste0("covariates/covar_all_unrelated.txt"), col.names = F, row.names = F, quote = F, sep = "\t")
```

### Subset again based on unrelated iids (use PLINK1.9)
`plink --bfile scfc_all --keep fid_iid_scfc_unrelated.txt --make-bed --out scfc_all_covar_unrelated`
```{r}
old_fam <- read.table("bfile/ABCD_all_old.fam")
colnames(old_fam) <- c("fid", "iid", "pid", "mid", "sex", "phenotype")

new_fam <- old_fam %>%
  left_join(fid_iid_scfc_unrelated, by = "iid") %>%
  mutate(fid = ifelse(is.na(fid.y), fid.x, fid.y)) %>%
  select(fid, iid, pid, mid, sex, phenotype)

write.table(new_fam, paste0("bfile/ABCD_all.fam"), row.names = F, col.names = F, quote = F, sep = "\t")

#现在做subset，做qc试试
parent_path <- '/Users/kurt/Documents/Data_Science_Project/0930_GWASplink20_standardized_noqc/'
dirpath <- '/Users/kurt/Documents/Data_Science_Project/0930_GWASplink20_standardized_noqc/'
plink_path <- "/Users/kurt/Documents/Data_Science_Project/0930_GWASplink20_standardized_noqc/"
# Subset by id
system(paste0(plink_path, "plink --bfile ", parent_path, "bfile/ABCD_all --keep ", dirpath, "bfile/fid_iid_scfc_unrelated.txt --make-bed --out ", dirpath, "bfile/scfc_all_unrelated"), intern = FALSE)
# NO QC
# system(paste0(plink_path, "plink --bfile ", dirpath, "bfile/scfc_all_unrelated --geno 0.1 --maf 0.05 --mind 0.1 --make-bed --out ", dirpath, "bfile/scfc_all_unrelated"), intern = FALSE)

# #再做一遍grm和sparse grm
# lib_path <- 'export DYLD_LIBRARY_PATH="/Users/kurt/Documents/Data_Science_Project/gcta-1.94.2-MacOS-ARM-x86_64/gcclib:$DYLD_LIBRARY_PATH"'
# system(lib_path, intern = TRUE)  # Set library path
# system(
#   paste0(plink_path, "gcta64 ",
#       "--bfile ", dirpath, "bfile/scfc_all_unrelated_qc ",
#       "--autosome  --make-grm  ", 
#       "--thread-num 16 ",
#       "--out ", dirpath, "bfile/scfc_all_unrelated_qc_out"), 
#       intern = F)
# system(
#   paste0(plink_path, "gcta64 ",
#       "--grm ", dirpath, "bfile/scfc_all_unrelated_qc_out ",
#       "--make-bK-sparse 0.05 ",
#       "--thread-num 16 ",
#       "--out ", dirpath, "bfile/scfc_all_unrelated_qc_sp_out"), 
#       intern = F)
```

### Do GWAS on PLINK2.0 --linear with --covar
```{r}
library(stringr)

files <- list.files(paste0(dirpath, "phenotype_roi/"))
phens <- files[str_detect(files, "\\.phen$")]
file_pairs <- setNames(paste0('gwas_', sub("\\.phen$", "", phens)), phens)

# print(length(file_pairs))
# print(file_pairs)

missing <- c(1:379)
for (phenotype_file in names(file_pairs)) {
  roi_i <- as.numeric(gsub(".*roi(\\d+)\\.phen", "\\1", phenotype_file))
  if (roi_i %in% missing) {
    out_file <- file_pairs[phenotype_file]
    # Define the path to the covariate file
    covar_path <- paste0(dirpath, "covariates/covar_all_unrelated.txt")
    command <- paste0(
        plink_path, "plink2 --bfile ", "/Users/kurt/Documents/Data_Science_Project/0930_GWASplink20_standardized_noqc/bfile/scfc_all_unrelated ",   #dirpath, "bfile/scfc_all_unrelated_qc ",
        "--pheno ", "/Users/kurt/Documents/Data_Science_Project/0930_GWASplink20_standardized_noqc/", "phenotype_roi/", phenotype_file, " ",
        "--covar ", "/Users/kurt/Documents/Data_Science_Project/0930_GWASplink20_standardized_noqc/covariates/covar_all_unrelated.txt", " ",
        "--glm no-x-sex hide-covar ",  # Added hide-covar to avoid covariate effect lines in the output
        "--covar-variance-standardize ",
        "--out ", dirpath, "gwas_results/", out_file
    )
    system(command)
    cat("GWAS command executed successfully for the phenotype file:", phenotype_file, "\n")
  }
}
```

### Read PLINK2.0 GWAS results
```{r}
for (i in missing) {
  filename <- paste0(dirpath, "gwas_results/gwas_scfc_unrelated_sd_harm2_family_roi", i, ".PHENO1.glm.linear")
  qassoc_data <- read.table(filename, header = F, sep = "\t")
  colnames(qassoc_data) <- c("#CHROM", "POS", "SNP", "REF", "ALT", "PROVISIONAL_REF?", "A1", "OMITTED", "A1_FREQ", "TEST", "OBS_CT", "BETA", "SE", "T_STAT", "P", "ERRCODE") # manually assign column names
  output_filename <- paste0(dirpath, "/gwas_results/gwas_unrelated_csv/gwas_scfc_unrelated_sd_harm2_family_roi", i, ".csv")
  write.csv(qassoc_data, output_filename, row.names = FALSE, quote = FALSE)
}
```
