---
title: "plot_scfc"
output: html_document
date: "2024-10-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**10/21: This is for plotting SCFC values after Fisher Transform and Harmonization on the brain**
**11/01: Added 1. plot SCFCs distribution to show skewness; 2. plot SCFC by networks**
**11/26: Plot demographics**
**03/07: Use new color scheme**
**03/20: Modify for Windows**
**03/22: Remove Brainstem**

## Read results and plot on brain regions
```{r}
## Plot ROIs on brain regions
########## Brain Visualization #########
library(ggseg)
library(ggplot2)
library(readxl)
library(dplyr)
library(tidyr)
### glasser atlas ########
### The first 360 regions of interest (ROIs) are from the Glasser atlas
### We will use ggsegGlasser to visulize them
library(ggsegGlasser)

### Load Utilities, data, tool and define directory
utilities_path <- "C:/Users/KurtJi/OneDrive - University of Illinois - Urbana/Desktop/UVA/DS_project/ABCD_data/ABCD_SCFC_utilities/"
bfile_path <- "C:/Users/KurtJi/OneDrive - University of Illinois - Urbana/Desktop/UVA/DS_project/ABCD_data/ABCD_bfile/"
cov_path <- "C:/Users/KurtJi/OneDrive - University of Illinois - Urbana/Desktop/UVA/DS_project/ABCD_data/Covariates/"
harm_path <- "C:/Users/KurtJi/OneDrive - University of Illinois - Urbana/Desktop/UVA/DS_project/ABCD_data/Harmonized_scfc/"
pheno_path <- "C:/Users/KurtJi/OneDrive - University of Illinois - Urbana/Desktop/UVA/DS_project/ABCD_data/Phenotype/"
tool_path <- "C:/Users/KurtJi/OneDrive - University of Illinois - Urbana/Desktop/UVA/DS_project/Tools/"

directory <- ""
load(paste0(utilities_path, "coupling_cbcl.RData"))
load(paste0(utilities_path, "scfc_coupling_matched.RData"))
# read ROI name, network and other files
network_df <- read_excel(paste0(utilities_path, "CAB-NP_v1.1_Labels-ReorderedbyNetworks.xlsx")) %>%
  rename(roi_num = INDEX) %>%
  mutate(ROI = paste0("roi",roi_num))
write.csv(network_df, paste0(directory, "network_df.csv"))
```

# 1126: Plot demographics
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

# Reshape the data to a long format for grouping and plotting, excluding "NA" levels
demo_long <- demo_cbcl_base_scfc %>%
  select(sex, race, ethn) %>%
  pivot_longer(cols = c(sex, race, ethn), names_to = "Variable", values_to = "Level") %>%
  filter(!is.na(Level) & Level != "NA")  # Exclude NA levels explicitly

# Define custom colors
custom_colors <- c("sex" = "skyblue", "race" = "lightgreen", "ethn" = "lightcoral")

# Create the bar plot
bar_plot <- ggplot(demo_long, aes(x = Level, fill = Variable)) +
  geom_bar(width = 0.75) +  # Create bars for each level
  facet_grid(~ Variable, scales = "free_x", space = "free") +  # Arrange variables side by side
  scale_fill_manual(values = custom_colors) +  # Set custom colors
  labs(title = "ABCD Study Demographic Information",
       x = "Level", y = "Count") +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels
    panel.grid.major.x = element_blank(),  # Clean grid lines between facets
    strip.text = element_text(face = "bold"),  # Bold facet labels
    legend.position = "none"  # Remove legend
  )

# Display the plot
print(bar_plot)

ggsave(paste0(directory, paste0("visualization/demo_info", ".png")), plot = bar_plot, width = 12, height = 8, dpi = 300)
```

## Plot!
```{r}
library(stringr)
mmp <- mmp_subcor[1:360] %>% str_remove(.,'_ROI') # remember to read coupling_cbcl.RData
person <- c(1:6381)
scfc_results <- paste0(harm_path, "alldf_trans_harm2.csv")
scfc_df <- read.csv(paste0(scfc_results)) %>%
  slice(person) %>% # select the first person's scfc values
  select(9:ncol(.)) %>%
  pivot_longer(cols = everything(), names_to = "ROI_name", values_to = "scfc_value") %>%
  mutate(ROI = paste0("roi", row_number()))
############################################################################
roi_glasser <- mmp %>% str_split(.,"_",simplify = TRUE) %>% data.frame()
colnames(roi_glasser) <- c("hemi","region")
roi_glasser <- roi_glasser %>% mutate(label=ifelse(hemi=='L',paste0("lh_L_",region), paste0("rh_R_",region)))
roi_glasser <- roi_glasser %>%
  tibble::rownames_to_column(var = "ROI") %>%
  mutate(ROI = paste0("roi", ROI))
roi_glasser <- roi_glasser %>%
  inner_join(scfc_df, by = "ROI")  # ROI is name

#===========================================================================
gldata <- tibble(
  label = roi_glasser$label,
  Estimate = roi_glasser[,6]
)
    
### cortical_position (i.e., how do we want the brain to be positioned)
cortical_pos <- c("left lateral", "right lateral","left medial","right medial")
### choose color palette
library(RColorBrewer)
# display.brewer.all()
color <- rev(brewer.pal(11, 'RdBu'))
library(scales)
# show_col(color)

### plot the coupling value in brain
plot <- gldata %>%
  ggplot() +
  geom_brain(atlas = glasser, 
             position = position_brain(cortical_pos), ### there is different options like "horizontal", "side ~ hemi"
             aes(fill = Estimate)) + scale_fill_gradient2(low = muted("blue"),
                                                          # mid = "gre",
                                                          high = muted("red"), #midpoint = 0.05, 
                                                          na.value = "white")+ggtitle("Glasser") +
                                                          theme_bw() +
                                                          theme(text = element_text(size = 10)) +
                                                          theme(panel.grid = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(),panel.border = element_blank()) +
                                                          theme(legend.position = 'bottom') + 
                                                          theme(legend.key.size = unit(1, 'cm'))

if (!dir.exists(paste0(directory, "visualization/"))) { # Save the plot to a file
  dir.create(paste0(directory, "visualization/"), recursive = F)
}
ggsave(paste0(directory, paste0("visualization/SCFC_person", person, "_glasser", ".png")), plot = plot, width = 10, height = 8, dpi = 300)
    
#=============================================================================
#### Get all data
subcor <- mmp_subcor[361:379] %>% str_remove(.,'_ROI') %>% str_split(.,'_',simplify = T) %>%as.data.frame()
colnames(subcor) <- c('region','hemi')

subcor <- subcor %>%
  tibble::rownames_to_column(var = "ROI") %>%
  mutate(ROI = paste0("roi", ROI)) %>%
  slice((n() - 18):n())  # 或者使用 tail(subcor, 19)，其实不用，只是验证

aseg$data$label
subcor$label <- paste0(str_to_title(subcor[,'hemi']), '-',str_to_title(subcor[,'region']))
subcor$label[19] <- 'Brain-Stem'
subcor$label[subcor$region=='thalamus'] <- paste0(subcor$label[subcor$region=='thalamus'],'-','Proper')
subcor$label[subcor$region=='diencephalon'] <- paste0(str_to_title(subcor$hemi[subcor$region=='diencephalon']),'-VentralDC')
subcor$label[subcor$region=='cerebellum'] <- paste0(subcor$label[subcor$region=='cerebellum'],'-','Cortex')

# Joining roi_glasser with assoc_df to align data
subcor <- subcor %>%
  inner_join(scfc_df, by = "ROI")  # ROI is name

gldata <- tibble(
  label = subcor$label,
  Estimate = subcor[,6]
)
plot <- gldata %>%
    #group_by(groups) %>%
    ggplot() +
    geom_brain(atlas = aseg, aes(fill = Estimate))+
    scale_fill_gradient2(low = muted("blue"),
                         mid = "white",
                         high = muted("red"),midpoint = 0, na.value = "white")+
    #ggtitle(paste(y_annot[i]))+
    theme_bw() +
    theme(panel.grid = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(),panel.border = element_blank())+
    theme(text = element_text(size = 15)) +
    theme(legend.position = 'bottom') + theme(legend.key.size = unit(1, 'cm'))

if (!dir.exists(paste0(directory, "visualization/"))) { # Save the plot to a file
  dir.create(paste0(directory, "visualization/"), recursive = F)
}
ggsave(paste0(directory, paste0("visualization/SCFC_person", person, "_glasser_subcor", ".png")), plot = plot, width = 10, height = 8, dpi = 300)
```
## Plot Distribution of SCFCs and ADHD
```{r}
library(stringr)
mmp <- mmp_subcor[1:360] %>% str_remove(.,'_ROI') # remember to read coupling_cbcl.RData
person <- 1
scfc_results <- paste0(harm_path, "alldf_trans_harm2.csv")
scfc_df <- read.csv(paste0(scfc_results)) %>%
  slice(person) %>% # select the first person's scfc values
  select(9:ncol(.)) %>%
  pivot_longer(cols = everything(), names_to = "ROI_name", values_to = "scfc_value") %>%
  mutate(ROI = paste0("roi", row_number()))
################################################################################
# Density plot of SCFC values to visualize skewness
scfc_density_plot <- ggplot(scfc_df, aes(x = scfc_value)) +  # Replace `SCFC_values` with the actual column name
  geom_density(fill = "#a8ddb5", alpha = 0.5) +  # Density plot with color fill
  labs(title = "Distribution of SCFC Values", x = "SCFC Values", y = "Density") +
  theme_minimal()

# Save the density plot
ggsave(filename = "visualization/scfc_distribution_plot.png", plot = scfc_density_plot, width = 8, height = 4)

################################################################################
adhd_df <- demo_cbcl_base_scfc %>%
  select(subjectkey, site_id_l, cbcl_scr_dsm5_adhd_t)

adhd_density_plot <- ggplot(adhd_df, aes(x = cbcl_scr_dsm5_adhd_t)) +  # Replace `SCFC_values` with the actual column name
  geom_density(fill = "#a8ddb5", alpha = 0.5) +  # Density plot with color fill
  labs(title = "Distribution of ADHD Scores", x = "ADHD Scores", y = "Density") +
  theme_minimal()

# Save the density plot
ggsave(filename = "visualization/adhd_distribution_plot.png", plot = adhd_density_plot, width = 8, height = 4)

#===============================================================================
adhd_histogram_plot <- ggplot(adhd_df, aes(x = cbcl_scr_dsm5_adhd_t)) +
  geom_histogram(fill = "#a8ddb5", color = "black", bins = 30, alpha = 0.7) +  # Histogram with custom bin width and color
  labs(title = "Distribution of ADHD Scores", x = "ADHD Scores", y = "Count") +
  theme_minimal()

# Save the histogram plot
ggsave(filename = "visualization/adhd_distribution_hist_plot.png", plot = adhd_histogram_plot, width = 8, height = 4)

```

### 02/15: Plot male vs. female
```{r}
adhd_df <- demo_cbcl_base_scfc %>%
  select(subjectkey, site_id_l, sex, cbcl_scr_dsm5_adhd_t)

adhd_density_plot <- ggplot(adhd_df, aes(x = cbcl_scr_dsm5_adhd_t, fill = sex)) +  
  geom_density(alpha = 0.5) +  # Transparent density for overlap
  scale_fill_manual(values = c("F" = "#FF9999", "M" = "#56B4E9")) +  # Custom colors for F & M
  labs(title = "Distribution of ADHD Scores by Sex", 
       x = "ADHD Scores", 
       y = "Density", 
       fill = "Sex") +  # Legend label
  theme_minimal() +
  theme(text = element_text(size = 12),
        legend.position = "right")  # Position legend to the right

# Print the plot
print(adhd_density_plot)

# Save the density plot
ggsave(filename = "visualization/adhd_distribution_fvm_plot.png", plot = adhd_density_plot, width = 8, height = 4)
```

################################################################################
## Plot ROIs by Network
```{r}
library(stringr)
person <- 1
scfc_results <- paste0(harm_path, "alldf_trans_harm2.csv")
scfc_df <- read.csv(paste0(scfc_results)) %>%
  slice(person) %>% # select the first person's scfc values
  select(9:ncol(.)) %>%
  pivot_longer(cols = everything(), names_to = "ROI_name", values_to = "scfc_value") %>%
  mutate(ROI = paste0("roi", row_number())) %>%
  left_join(network_df[1:360,], by = "ROI")
```

```{r}
scfc_df <- scfc_df %>%
  mutate(NETWORK = case_when(
    NETWORK == "Visual1" ~ "Visual1 (VIS1)",
    NETWORK == "Visual2" ~ "Visual2 (VIS2)",
    NETWORK == "Somatomotor" ~ "Somatomotor (SMN)",
    NETWORK == "Cingulo-Opercular" ~ "Cingulo-Opercular (CON)",
    NETWORK == "Dorsal-Attention" ~ "Dorsal-Attention (DAN)",
    NETWORK == "Language" ~ "Language (LANG)",
    NETWORK == "Frontoparietal" ~ "Frontoparietal (FPN)",
    NETWORK == "Auditory" ~ "Auditory (AUD)",
    NETWORK == "Posterior-Multimodal" ~ "Posterior-Multimodal (PMN)",
    NETWORK == "Default" ~ "Default (DMN)",
    NETWORK == "Orbito-Affective" ~ "Orbito-Affective (OAN)",
    NETWORK == "Ventral-Multimodal" ~ "Ventral-Multimodal (VMN)",
    TRUE ~ NETWORK  # Keep unchanged if not in the list
  )) %>%
  mutate(NETWORK = ifelse(is.na(NETWORK), "Subcortical (SUBC)", NETWORK))

# Preserve existing colors but replace SUBC with a new color
network_colors <- c(
  "Default (DMN)" = "#55a9d1",         # Light Blue
  "Cingulo-Opercular (CON)" = "#7474cb", # Light Orange
  "Dorsal-Attention (DAN)" = "#69b842",  # Light Green
  "Somatomotor (SMN)" = "#9da13f",       # Light Purple
  "Language (LANG)" = "#9f1700",        # Light Red
  "Visual2 (VIS2)" = "#d0406d",         # Light Peach
  "Frontoparietal (FPN)" = "#133d86",    # Light Indigo
  "Subcortical (SUBC)" = "#cc5c40",     # Light Pastel Green (new color)
  "Auditory (AUD)" = "#d1a348"          # Light Coral
)

# Assign new colors for additional networks
extra_network_colors <- c(
  "Visual1 (VIS1)" = "#FFB6C1",         # Light Pink
  "Posterior-Multimodal (PMN)" = "#1a6f60", # Soft Lime
  "Orbito-Affective (OAN)" = "#bc6173",  # Light Lavender
  "Ventral-Multimodal (VMN)" = "#8DD3C7" # Light Cyan
)

# Merge into a single color palette
network_colors <- c(network_colors, extra_network_colors)

# Prepare roi_glasser data
roi_glasser <- (mmp_subcor[1:379] %>% str_remove(.,'_ROI')) %>% # remember to read coupling_cbcl.RData %>% 
  str_split(.,"_",simplify = TRUE) %>% 
  data.frame() %>%
  setNames(c("hemi","region")) %>%
  tibble::rownames_to_column(var = "roi_num") %>%
  mutate(roi_num = as.integer(roi_num),
         label = ifelse(hemi == 'L', paste0("lh_L_", region), paste0("rh_R_", region)))

# Join data and map network colors
roi_glasser <- roi_glasser %>%
  inner_join(scfc_df, by = "roi_num")

# Data for plotting
gldata <- tibble(
  label = roi_glasser$label,
  Estimate = roi_glasser$scfc_value,
  NETWORK = roi_glasser$NETWORK  # Use NETWORK as a factor for color mapping
)

# Define brain view positions
cortical_pos <- c("left lateral", "right lateral", "left medial", "right medial")

# Plot with network colors and legend
plot <- gldata %>%
  ggplot() +
  geom_brain(
    atlas = glasser, 
    position = position_brain(side ~ hemi), 
    aes(fill = NETWORK)
  ) +
  scale_fill_manual(values = network_colors, na.value = "#c7c7c7") +  # Map NETWORK to colors with a legend
  labs(fill = "Network") +  # Change legend title
  theme_bw() +
  theme(
    text = element_text(size = 10),
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    legend.position = 'bottom',  # Position the legend at the bottom
    legend.key.size = unit(1, 'cm')
  )

print(plot)

# Save the plot
ggsave(filename = paste0("visualization/cortical_network", ".png"), plot = plot, width = 10, height = 8, dpi = 300)

#########################################################################################################################

# Joining roi_glasser with assoc_df to align data
#### Get all data
subcor <- mmp_subcor[361:379] %>% str_remove(.,'_ROI') %>% str_split(.,'_',simplify = T) %>%as.data.frame()
colnames(subcor) <- c('region','hemi')

#################################################
# Remove Brainstem from data
subcor <- subcor[1:18,]
#################################################

subcor <- subcor %>%
  tibble::rownames_to_column(var = "ROI") %>%
  mutate(ROI = as.numeric(ROI)) %>%
  mutate(ROI = 360 + ROI) %>%
  mutate(ROI = paste0("roi", ROI)) %>%
  slice((n() - 18):n()) # 或者使用 tail(subcor, 19)，其实不用，只是验证

subcor <- subcor %>%
  inner_join(scfc_df, by = "ROI")  # ROI is name


aseg$data$label
subcor$label <- paste0(str_to_title(subcor[,'hemi']), '-',str_to_title(subcor[,'region']))
#subcor$label[19] <- 'Brain-Stem'
subcor$label[subcor$region=='thalamus'] <- paste0(subcor$label[subcor$region=='thalamus'],'-','Proper')
subcor$label[subcor$region=='diencephalon'] <- paste0(str_to_title(subcor$hemi[subcor$region=='diencephalon']),'-VentralDC')
subcor$label[subcor$region=='cerebellum'] <- paste0(subcor$label[subcor$region=='cerebellum'],'-','Cortex')

gldata <- tibble(
  label = subcor$label,
  NETWORK = subcor$NETWORK
)

plot <- gldata %>%
    #group_by(groups) %>%
    ggplot() +
    geom_brain(atlas = aseg, 
               aes(fill = NETWORK)
               ) +
    scale_fill_manual(values = network_colors, na.value = "#c7c7c7") +
    labs(fill = "Network") +  # Change legend title
    #ggtitle(paste(y_annot[i]))+
    theme_bw() +
    theme(panel.grid = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(),panel.border = element_blank())+
    theme(text = element_text(size = 10)) +
    theme(legend.position = 'bottom') + theme(legend.key.size = unit(1, 'cm'))

if (!dir.exists(paste0(directory, "visualization/"))) { # Save the plot to a file
  dir.create(paste0(directory, "visualization/"), recursive = F)
}

print(plot)

ggsave(paste0(directory, paste0("visualization/subcortical_network", ".png")), plot = plot, width = 10, height = 8, dpi = 300)

```

```{r}
colors <- c("#FFC0CB",  # Bright Red
            "#FFE4E1",  # Bright Green
            "#00FFFF",  # Bright Blue
            "#ffff76",  # Bright Yellow
            "#00008B",  # Magenta
            "#E31A1C",  # Cyan
            "#FFA500",  # Orange
            "#800080",  # Purple
            "#008000",  # Dark Green
            "#1E90FF",  # Pink
            "#A52A2A",  # Brown
            "#a8ddb5")  # Black

unique_networks <- unique(scfc_df$NETWORK)
network_colors <- setNames(colors[1:length(unique_networks)], unique_networks)

scfc_df <- scfc_df %>%
  mutate(NETWORK = factor(NETWORK, levels = unique_networks))

# Prepare roi_glasser data
roi_glasser <- mmp %>% 
  str_split(.,"_",simplify = TRUE) %>% 
  data.frame() %>%
  setNames(c("hemi","region")) %>%
  tibble::rownames_to_column(var = "roi_num") %>%
  mutate(roi_num = as.integer(roi_num),
         label = ifelse(hemi == 'L', paste0("lh_L_", region), paste0("rh_R_", region)))

# Join data and map network colors
roi_glasser <- roi_glasser %>%
  inner_join(scfc_df, by = "roi_num")

# Data for plotting
gldata <- tibble(
  label = roi_glasser$label,
  Estimate = roi_glasser$scfc_value,
  NETWORK = roi_glasser$NETWORK  # Use NETWORK as a factor for color mapping
)

# Define brain view positions
cortical_pos <- c("left lateral", "right lateral", "left medial", "right medial")

# Plot with network colors and legend
plot <- gldata %>%
  ggplot() +
  geom_brain(
    atlas = glasser, 
    position = position_brain(cortical_pos), 
    aes(fill = NETWORK)
  ) +
  scale_fill_manual(values = network_colors) +  # Map NETWORK to colors with a legend
  ggtitle("Cortical Network") +
  theme_bw() +
  theme(
    text = element_text(size = 10),
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    legend.position = 'bottom',  # Position the legend at the bottom
    legend.key.size = unit(1, 'cm')
  )

# Save the plot
ggsave(filename = paste0(base_path, "visualization/cortical_network", ".png"), plot = plot, width = 10, height = 8, dpi = 300)

################################################################################
unique_networks <- unique(scfc_df$NETWORK)
network_colors <- setNames(colors[1:length(unique_networks)], unique_networks)
subcor <- mmp_subcor %>%
  str_remove('_ROI') %>%
  str_split('_', simplify = TRUE) %>%
  as.data.frame()
colnames(subcor) <- c('region', 'hemi')
subcor <- subcor %>%
  tibble::rownames_to_column(var = "ROI") %>%
  mutate(ROI = paste0("", ROI)) %>%
  slice((n() - 18):n())  # Select last 19 ROIs

subcor$label <- paste0(str_to_title(subcor$hemi), '-', str_to_title(subcor$region))
subcor$label[19] <- 'Brain-Stem'
subcor$label[subcor$region == 'thalamus'] <- paste0(subcor$label[subcor$region == 'thalamus'], '-Proper')
subcor$label[subcor$region == 'diencephalon'] <- paste0(str_to_title(subcor$hemi[subcor$region == 'diencephalon']), '-VentralDC')
subcor$label[subcor$region == 'cerebellum'] <- paste0(subcor$label[subcor$region == 'cerebellum'], '-Cortex')

subcor <- subcor %>%
  mutate(roi_num = as.integer(ROI)) %>%
  inner_join(scfc_df, by = "roi_num") %>%
  mutate(NETWORK = factor(NETWORK, levels = unique_networks))

testdata <- tibble(
  label = subcor$label,
  h2 = subcor$scfc_value,
  NETWORK = subcor$NETWORK
)
plot <- testdata %>%
  ggplot() +
  geom_brain(
    atlas = aseg,
    aes(fill = NETWORK)
  ) +
  scale_fill_manual(values = network_colors) +  # Apply custom colors to each network
  ggtitle("Subcortical Networks") +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    legend.position = 'bottom',
    legend.key.size = unit(1, 'cm'),
    text = element_text(size = 15)
  )

# Save the plot
ggsave(filename = paste0(base_path, "visualization/subcortical_network", ".png"), plot = plot, width = 10, height = 8, dpi = 300)
```

################################################################################
## Plot ROIs by Hemisphere
```{r}
library(stringr)
person <- 1
scfc_results <- paste0(harm_path, "alldf_trans_harm2.csv")
scfc_df <- read.csv(paste0(scfc_results)) %>%
  slice(person) %>% # select the first person's scfc values
  select(9:ncol(.)) %>%
  pivot_longer(cols = everything(), names_to = "ROI_name", values_to = "scfc_value") %>%
  mutate(ROI = paste0("roi", row_number())) %>%
  inner_join(network_df, by = "ROI")
```

```{r}
colors <- c("#FFC0CB",  # Bright Red
            "#FFE4E1",  # Bright Green
            "#00FFFF",  # Bright Blue
            "#ffff76",  # Bright Yellow
            "#00008B",  # Magenta
            "#E31A1C",  # Cyan
            "#FFA500",  # Orange
            "#800080",  # Purple
            "#008000",  # Dark Green
            "#1E90FF",  # Pink
            "#A52A2A",  # Brown
            "#a8ddb5")  # Black

unique_networks <- unique(scfc_df$NETWORK)
network_colors <- setNames(colors[1:length(unique_networks)], unique_networks)

scfc_df <- scfc_df %>%
  mutate(NETWORK = factor(NETWORK, levels = unique_networks))

# Prepare roi_glasser data
roi_glasser <- mmp %>% 
  str_split(.,"_",simplify = TRUE) %>% 
  data.frame() %>%
  setNames(c("hemi","region")) %>%
  tibble::rownames_to_column(var = "roi_num") %>%
  mutate(roi_num = as.integer(roi_num),
         label = ifelse(hemi == 'L', paste0("lh_L_", region), paste0("rh_R_", region)))

# Join data and map network colors
roi_glasser <- roi_glasser %>%
  inner_join(scfc_df, by = "roi_num")

# Data for plotting
gldata <- tibble(
  label = roi_glasser$label,
  Estimate = roi_glasser$scfc_value,
  NETWORK = roi_glasser$NETWORK  # Use NETWORK as a factor for color mapping
)

# Define brain view positions
cortical_pos <- c("left lateral", "right lateral", "left medial", "right medial")

# Plot with network colors and legend
plot <- gldata %>%
  ggplot() +
  geom_brain(
    atlas = glasser, 
    position = position_brain(cortical_pos), 
    aes(fill = NETWORK)
  ) +
  scale_fill_manual(values = network_colors) +  # Map NETWORK to colors with a legend
  ggtitle("Cortical Network") +
  theme_bw() +
  theme(
    text = element_text(size = 10),
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    legend.position = 'bottom',  # Position the legend at the bottom
    legend.key.size = unit(1, 'cm')
  )

# Save the plot
ggsave(filename = paste0(base_path, "visualization/cortical_network", ".png"), plot = plot, width = 10, height = 8, dpi = 300)

################################################################################
unique_networks <- unique(scfc_df$NETWORK)
network_colors <- setNames(colors[1:length(unique_networks)], unique_networks)
subcor <- mmp_subcor %>%
  str_remove('_ROI') %>%
  str_split('_', simplify = TRUE) %>%
  as.data.frame()
colnames(subcor) <- c('region', 'hemi')
subcor <- subcor %>%
  tibble::rownames_to_column(var = "ROI") %>%
  mutate(ROI = paste0("", ROI)) %>%
  slice((n() - 18):n())  # Select last 19 ROIs

subcor$label <- paste0(str_to_title(subcor$hemi), '-', str_to_title(subcor$region))
subcor$label[19] <- 'Brain-Stem'
subcor$label[subcor$region == 'thalamus'] <- paste0(subcor$label[subcor$region == 'thalamus'], '-Proper')
subcor$label[subcor$region == 'diencephalon'] <- paste0(str_to_title(subcor$hemi[subcor$region == 'diencephalon']), '-VentralDC')
subcor$label[subcor$region == 'cerebellum'] <- paste0(subcor$label[subcor$region == 'cerebellum'], '-Cortex')

subcor <- subcor %>%
  mutate(roi_num = as.integer(ROI)) %>%
  inner_join(scfc_df, by = "roi_num") %>%
  mutate(NETWORK = factor(NETWORK, levels = unique_networks))

testdata <- tibble(
  label = subcor$label,
  h2 = subcor$scfc_value,
  NETWORK = subcor$NETWORK
)
plot <- testdata %>%
  ggplot() +
  geom_brain(
    atlas = aseg,
    aes(fill = NETWORK)
  ) +
  scale_fill_manual(values = network_colors) +  # Apply custom colors to each network
  ggtitle("Subcortical Networks") +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.border = element_blank(),
    legend.position = 'bottom',
    legend.key.size = unit(1, 'cm'),
    text = element_text(size = 15)
  )

# Save the plot
ggsave(filename = paste0(base_path, "visualization/subcortical_network", ".png"), plot = plot, width = 10, height = 8, dpi = 300)
```

```{r}
  # #-------------------------------------------plot first 360 ROIs----------------------------------------------------------
  # roi_glasser <- roi_glasser %>%
  #   inner_join(scfc_df, by = "ROI")
  # 
  # gldata <- tibble(
  #   label = roi_glasser$label,
  #   Estimate = roi_glasser$h_2,
  # )
  # ### cortical_position (i.e., how do we want the brain to be positioned)
  # cortical_pos <- c("left lateral", "right lateral","left medial","right medial")
  # ##### plot the coupling value in brain
  # min_value <- min(gldata$Estimate, na.rm = TRUE)
  # quantiles <- quantile(gldata$Estimate, probs = c(0.5), na.rm = TRUE)
  # max_value <- max(gldata$Estimate, na.rm = TRUE)
  # plot <- gldata %>%
  #   ggplot() +
  #   geom_brain(
  #     atlas = glasser, 
  #     position = position_brain(cortical_pos), # side ~ hemi
  #     # aes(fill = Estimate)) + scale_fill_gradientn(colours = cl, na.value = "#e8e8e8",
  #     #                                               breaks = c(0),
  #     #                                               labels = c(paste0("Min: ", round(min_value, 2)), 
  #     #                                                          paste0("Median: ", round(quantiles[1], 2)),
  #     #                                                          paste0("Max: ", round(max_value, 2)))
  #     #                                             ) + ggtitle("Glasser") + 
  #     aes(fill = Estimate)) + scale_fill_gradientn(colours = cl, #midpoint = 0.05,
  #                                                   na.value = "#d6d6d6", 
  #                                                   breaks=c(min_value, quantiles[1], max_value),
  #                                                   labels=c(round(min_value,2), round(quantiles[1],2), round(max_value,2)),
  #                                                   limits=c(min_value, max_value)) + ggtitle("Heritability (FDR < 0.05)") +
  #   theme_bw() + 
  #   theme(text = element_text(size = 10)) + 
  #   theme(panel.grid = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(),panel.border = element_blank()) +
  #   theme(legend.position = 'bottom') + theme(legend.key.size = unit(1, 'cm')) + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + 
  #   theme()
  # 
  # ggsave(paste0(base_path, "visualization/herit_cortical_harm",harm,"_filtbh.png"), plot = plot, width = 10, height = 8, dpi = 300)
  # 
  # #-------------------------------------------plot last 19 ROIs----------------------------------------------------------
  # ### plot subcortical
  # #### Get all data
  # subcor <- mmp_subcor %>% str_remove(.,'_ROI') %>% str_split(.,'_',simplify = T) %>% data.frame()
  # colnames(subcor) <- c('region','hemi')
  # subcor <- subcor %>%
  #   tibble::rownames_to_column(var = "ROI") %>%
  #   mutate(ROI = paste0("",ROI)) %>%
  #   slice((n() - 18):n())  # 或者使用 tail(subcor, 19)
  # 
  # aseg$data$label
  # subcor$label <- paste0(str_to_title(subcor[,'hemi']), '-',str_to_title(subcor[,'region']))
  # subcor$label[19] <- 'Brain-Stem'
  # subcor$label[subcor$region=='thalamus'] <- paste0(subcor$label[subcor$region=='thalamus'],'-','Proper')
  # subcor$label[subcor$region=='diencephalon'] <- paste0(str_to_title(subcor$hemi[subcor$region=='diencephalon']),'-VentralDC')
  # subcor$label[subcor$region=='cerebellum'] <- paste0(subcor$label[subcor$region=='cerebellum'],'-','Cortex')
  # 
  # # Joining roi_glasser with ivw_df to align data
  # subcor <- subcor %>%
  #   mutate(ROI = as.integer(ROI)) %>%
  #   inner_join(scfc_harm_df, by = "ROI")
  # 
  # testdata <- tibble(
  #   label = subcor$label,
  #   h2 = subcor$h_2
  # )
  # plot <- testdata %>%
  #   #group_by(groups) %>%
  #   ggplot() +
  #   geom_brain(atlas = aseg, aes(fill = h2))+
  #   scale_fill_gradientn(#low = muted("lightgreen"),
  #                        # # mid = "white",
  #                        # high = muted("darkgreen"),midpoint = 0, 
  #                        colours = cl,
  #                        na.value = "#d6d6d6", 
  #                        breaks=c(min_value, quantiles[1], max_value),
  #                                                   labels=c(round(min_value,2), round(quantiles[1],2), round(max_value,2)),
  #                                                   limits=c(min_value, max_value)) + ggtitle("Heritability (FDR p < 0.05)") + 
  #   #ggtitle(paste(y_annot[i]))+
  #   theme_bw() +
  #   theme(panel.grid = element_blank(),axis.text = element_blank(),axis.ticks = element_blank(),panel.border = element_blank())+
  #   theme(text = element_text(size = 15)) +
  #   theme(legend.position = 'bottom') + theme(legend.key.size = unit(1, 'cm')) + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))
  # 
  # ggsave(paste0(base_path, "visualization/herit_subcortical_harm",harm,"_filtbh.png"), plot = plot, width = 10, height = 8, dpi = 300)

```